---
title: "Risk Data Analyst - Talk Exercise"
subtitle: "Two SQL challenges to practice your fraud analytics perspective"
description-meta: "Two SQL challenges to practice your fraud analytics perspective"
format: html
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE)
```

```{r, echo = FALSE}
library(odbc)
library(DBI)
library(downloadthis)

sqlconn <- dbConnect(odbc(),
                      Driver = "SQL Server",
                      Server = "localhost\\SQLEXPRESS",
                      Database = "master")
```


<meta name="twitter:card" content="featured.png" />
<meta property="og:description" content="Two SQL challenges to practice your fraud analytics perspective" />
<meta name="twitter:image" content="featured.png" />
<meta property="og:image" content="featured.png" />


Hi there,

This page contains two fake exercises we'll (partially) go over in my talk about Fraud Analytics.

If you have the time and energy, give the exercises a try before the talk!

</br>

-----

### 1. Bot Registrations

> We received an alert about a spike in registration in partner X, can you look into it to see if you identify a bot/fraudulant group registering together?

<details>

<summary>Hint</summary>

Try searching for a specific pattern in the Name/Email/Registration date by which you can group users together.

</details>

Here's the top 10 rows:

```{sql, connection = 'sqlconn'}
SELECT TOP 10 *
FROM user_registrations
```

Here's the code to generate the table (you can find a copy symbol on the right top of the code chunk):

```{sql, eval=  FALSE, attr.source='style="max-height: 200px;overflow: scroll;"', connection='sqlconn'}
CREATE TABLE user_registrations 
(
    first_name	VARCHAR(512),
    last_name	VARCHAR(512),
    email	VARCHAR(512),
    registration_date	VARCHAR(512)
);

INSERT INTO user_registrations (first_name, last_name, email, registration_date) VALUES
	('Clemmy', 'Lezemere', 'clezemere1e@yolasite.com', '2024-01-01'),
	('Rolando', 'Woonton', 'rwoonton2s@addthis.com', '2024-01-01'),
	('Ervin', 'Ponde', 'eponde3b@shutterfly.com', '2024-01-01'),
	('Emanuel', 'Pepperill', 'epepperill3u@phpbb.com', '2024-01-01'),
	('Helen-elizabeth', 'Shropsheir', 'hshropsheir5c@mlb.com', '2024-01-01'),
	('Josi', 'Aindrais', 'jaindrais61@dagondesign.com', '2024-01-01'),
	('Denise', 'Dripp', 'ddripp6z@ning.com', '2024-01-01'),
	('Dorthy', 'Jamieson', 'djamieson7j@360.cn', '2024-01-01'),
	('Blane', 'Cocking', 'bcocking7z@reference.com', '2024-01-01'),
	('Linus', 'Wantling', 'lwantling86@patch.com', '2024-01-01'),
	('Geralda', 'Deadman', 'bsikdar@yahoo.com', '2024-01-01'),
	('Nisse', 'Saberton', 'rcwil@yahoo.com', '2024-01-01'),
	('Ardisj', 'Bourthoumieux', 'bruck@hotmail.com', '2024-01-01'),
	('Calli', 'Desorts', 'wenzlaff@gmail.com', '2024-01-01'),
	('Theodor', 'Masarrat', 'msusa@hotmail.com', '2024-01-01'),
	('Ainsley', 'Pittam', 'liedra@yahoo.com', '2024-01-01'),
	('Felicity', 'Tape', 'zyghom@hotmail.com', '2024-01-01'),
	('Tess', 'Samart', 'mrdvt@gmail.com', '2024-01-01'),
	('Chauncey', 'Lynagh', 'sylvan.schumm@yahoo.com', '2024-01-01'),
	('Dita', 'Siveter', 'egleichner@hotmail.com', '2024-01-01'),
	('Ivan', 'Kaas', 'korbin57@yahoo.com', '2024-01-01'),
	('Deanne', 'Metterick', 'smith.makenna@yahoo.com', '2024-01-01'),
	('Moss', 'Cave', 'jdicki@hotmail.com', '2024-01-01'),
	('Natalya', 'Brissenden', 'lcorkery@gmail.com', '2024-01-01'),
	('Marilee', 'Beldon', 'oral65@yahoo.com', '2024-01-01'),
	('Lorine', 'Siddall', 'twintheiser@gmail.com', '2024-01-01'),
	('Sansone', 'Alexandersson', 'salexandersson8c@exblog.jp', '2024-01-02'),
	('Illa', 'Lecount', 'ilecount8l@slashdot.org', '2024-01-02'),
	('Marmaduke', 'Rolstone', 'mrolstone93@wufoo.com', '2024-01-02'),
	('Betti', 'Lafontaine', 'blafontaineah@jigsy.com', '2024-01-02'),
	('Kelbee', 'Wilmington', 'kwilmingtonap@wisc.edu', '2024-01-02'),
	('Pierrette', 'Orpyne', 'porpynear@unblog.fr', '2024-01-02'),
	('Joanna', 'Thiolier', 'jthiolierat@fotki.com', '2024-01-02'),
	('Fidelia', 'Hyatt', 'fhyattbr@samsung.com', '2024-01-02'),
	('Pansy', 'Stiling', 'pstilingbw@jigsy.com', '2024-01-02'),
	('Aryn', 'Wackly', 'awacklyc3@imdb.com', '2024-01-02'),
	('Ellwood', 'Fearnyhough', 'efearnyhoughdj@hp.com', '2024-01-02'),
	('Dorita', 'Tuftin', 'dtuftine7@scientificamerican.com', '2024-01-02'),
	('Cate', 'Feaster', 'cfeasterf5@dedecms.com', '2024-01-02'),
	('Sileas', 'Marquese', 'smarquesefs@seattletimes.com', '2024-01-02'),
	('Anneliese', 'Jeanneau', 'ajeanneaugk@weebly.com', '2024-01-02'),
	('George', 'Citrine', 'gcitrinegl@deviantart.com', '2024-01-02'),
	('Oren', 'Pauling', 'opaulingh2@harvard.edu', '2024-01-02'),
	('Damiano', 'Diess', 'ddiesshe@buzzfeed.com', '2024-01-02'),
	('Ashla', 'Drage', 'adrageiz@51.la', '2024-01-02'),
	('Irita', 'Pedrollo', 'ipedrollojd@deviantart.com', '2024-01-02'),
	('Fania', 'Fudger', 'ffudger4@apple.com', '2024-01-02'),
	('Bennie', 'McCurrie', 'bmccurrieg@amazon.de', '2024-01-02'),
	('Faun', 'Mead', 'fmeadk@plala.or.jp', '2024-01-02'),
	('Andie', 'Hearsum', 'ahearsum21@cmu.edu', '2024-01-02'),
	('Aguste', 'Taylder', 'ataylder22@auda.org.au', '2024-01-02'),
	('Kristoforo', 'Shapero', 'kshapero27@fda.gov', '2024-01-02'),
	('Shelly', 'Loughrey', 'sloughrey2t@japanpost.jp', '2024-01-02'),
	('Lorena', 'Arkley', 'larkley54@upenn.edu', '2024-01-02'),
	('Ingunna', 'Mahony', 'imahony5q@ehow.com', '2024-01-02'),
	('Oliver', 'De Laspee', 'odelaspee62@house.gov', '2024-01-02'),
	('Noel', 'Biermatowicz', 'nbiermatowicz6i@wp.com', '2024-01-02'),
	('Margit', 'Ledbetter', 'mledbetter7v@vistaprint.com', '2024-01-02'),
	('Teresita', 'Strickland', 'tstrickland7y@gmpg.org', '2024-01-02'),
	('Clare', 'Duer', 'cduer83@theglobeandmail.com', '2024-01-02'),
	('Riannon', 'Cowser', 'rcowser96@sun.com', '2024-01-02'),
	('Dallas', 'Bufton', 'dbuftona2@webs.com', '2024-01-02'),
	('Blancha', 'Ivanilov', 'bivanilovay@kickstarter.com', '2024-01-02'),
	('Spence', 'Lealle', 'slealleb8@ucoz.ru', '2024-01-02'),
	('Zelig', 'Carvil', 'zcarvild3@soundcloud.com', '2024-01-02'),
	('Jocelyn', 'Yukhnev', 'jyukhneve0@europa.eu', '2024-01-02'),
	('Eal', 'Greiswood', 'egreiswoodem@ehow.com', '2024-01-02'),
	('Rafa', 'Pinfold', 'rpinfoldet@baidu.com', '2024-01-02'),
	('Timothea', 'Whiteford', 'twhitefordex@icio.us', '2024-01-02'),
	('Swen', 'Oldershaw', 'soldershawff@github.com', '2024-01-02'),
	('Gretta', 'Blakelock', 'gblakelockgu@hhs.gov', '2024-01-02'),
	('Vida', 'Guilder', 'vguilderh7@naver.com', '2024-01-02'),
	('Adams', 'Toffoloni', 'atoffolonihi@merriam-webster.com', '2024-01-02'),
	('Ashli', 'Wooler', 'awoolerhn@theguardian.com', '2024-01-02'),
	('Flory', 'Assaf', 'fassafiy@mapy.cz', '2024-01-02'),
	('Selma', 'Larvin', 'violinhi@yahoo.com', '2024-01-02'),
	('Amory', 'Latham', 'vlefevre@gmail.com', '2024-01-02'),
	('Yoko', 'Eck', 'dialworld@hotmail.com', '2024-01-02'),
	('Cherilyn', 'Lawther', 'smartfart@gmail.com', '2024-01-02'),
	('Lanita', 'Matityahu', 'quinn@gmail.com', '2024-01-02'),
	('Malvin', 'Mallett', 'wbarker@hotmail.com', '2024-01-02'),
	('Garey', 'Relf', 'rmcfarla@hotmail.com', '2024-01-02'),
	('Valeria', 'Carmel', 'dawson.kiehn@gmail.com', '2024-01-02'),
	('Fawnia', 'Sparsholt', 'geo.johnston@hotmail.com', '2024-01-02'),
	('Cobby', 'Espinoza', 'lauren.mckenzie@hotmail.com', '2024-01-02'),
	('Angelique', 'Howgego', 'shields.daryl@gmail.com', '2024-01-02'),
	('Geoffry', 'Sacchetti', 'pauline81@yahoo.com', '2024-01-02'),
	('Kaela', 'Olin', 'mayert.kelley@yahoo.com', '2024-01-02'),
	('Kaitlynn', 'McCarly', 'gleason.myah@gmail.com', '2024-01-02'),
	('Kay', 'Trimbey', 'horacio52@hotmail.com', '2024-01-02'),
	('Josh', 'Monelli', 'ftreutel@gmail.com', '2024-01-02'),
	('Hermina', 'Conti', 'hconti17@samsung.com', '2024-01-03'),
	('Aurilia', 'Shone', 'ashone1y@constantcontact.com', '2024-01-03'),
	('Andria', 'OMahoney', 'aomahoney2j@quantcast.com', '2024-01-03'),
	('Clemente', 'Fullun', 'cfullun78@slate.com', '2024-01-03'),
	('Cheri', 'Janas', 'cjanas7s@gizmodo.com', '2024-01-03'),
	('Veda', 'Caslett', 'vcaslett7w@topsy.com', '2024-01-03'),
	('Arny', 'Iddiens', 'aiddiens8i@people.com.cn', '2024-01-03'),
	('Arluene', 'Gomes', 'agomes8u@surveymonkey.com', '2024-01-03'),
	('Susanetta', 'Indgs', 'sindgs95@so-net.ne.jp', '2024-01-03'),
	('Cammy', 'Miner', 'cminer97@twitpic.com', '2024-01-03'),
	('Morry', 'McMullen', 'mmcmullena8@princeton.edu', '2024-01-03'),
	('Genovera', 'Casel', 'gcaselb3@cocolog-nifty.com', '2024-01-03'),
	('Vina', 'Tinkham', 'vtinkhambc@sakura.ne.jp', '2024-01-03'),
	('Laverne', 'Sibbit', 'lsibbitbp@dedecms.com', '2024-01-03'),
	('Gilemette', 'Conford', 'gconforde6@msu.edu', '2024-01-03'),
	('Sander', 'Jerzykiewicz', 'sjerzykiewiczeu@wikispaces.com', '2024-01-03'),
	('Hermina', 'Molden', 'hmoldenfp@cnbc.com', '2024-01-03'),
	('Sianna', 'Derham', 'sderhamg9@bandcamp.com', '2024-01-03'),
	('Sasha', 'Willoughley', 'swilloughleyga@dot.gov', '2024-01-03'),
	('Diena', 'Pigford', 'dpigfordh9@github.com', '2024-01-03'),
	('Ester', 'Insull', 'einsullhu@ebay.com', '2024-01-03'),
	('Reena', 'Noad', 'rnoadhv@washingtonpost.com', '2024-01-03'),
	('Merralee', 'Broker', 'mbrokerhy@cargocollective.com', '2024-01-03'),
	('Johny', 'Charity', 'suresh@hotmail.com', '2024-01-03'),
	('Jameson', 'Gever', 'arathi@gmail.com', '2024-01-03'),
	('Karie', 'Stanlake', 'portscan@hotmail.com', '2024-01-03'),
	('Olivette', 'Twidell', 'lushe@yahoo.com', '2024-01-03'),
	('Trudey', 'Cammock', 'boomzilla@gmail.com', '2024-01-03'),
	('Garold', 'Haythorn', 'harpes@yahoo.com', '2024-01-03'),
	('Templeton', 'McGairl', 'vbahringer@yahoo.com', '2024-01-03'),
	('Clemmie', 'Gunbie', 'dondricka@hotmail.com', '2024-01-03'),
	('Yuma', 'Scurrah', 'ygoyette@gmail.com', '2024-01-03'),
	('Alison', 'Krug', 'kreiger.arne@gmail.com', '2024-01-03'),
	('Haskel', 'Gainsborough', 'lwisoky@yahoo.com', '2024-01-03'),
	('Antoni', 'Oxterby', 'fgreen@gmail.com', '2024-01-03'),
	('Curtis', 'Blazhevich', 'bkuhlman@hotmail.com', '2024-01-03'),
	('Adoree', 'Rosenfelt', 'schuppe.juana@hotmail.com', '2024-01-03'),
	('Alaric', 'Rearden', 'arearden6@soup.io', '2024-01-04'),
	('Bryce', 'Peasby', 'bpeasbyt@photobucket.com', '2024-01-04'),
	('Demetri', 'Riddiough', 'driddioughz@wufoo.com', '2024-01-04'),
	('Sonya', 'Corwin', 'scorwin1h@goo.ne.jp', '2024-01-04'),
	('Dacy', 'Cottom', 'dcottom1p@gnu.org', '2024-01-04'),
	('Rodney', 'Hofner', 'rhofner1x@acquirethisname.com', '2024-01-04'),
	('Raina', 'Hanbury-Brown', 'rhanburybrown26@livejournal.com', '2024-01-04'),
	('Lib', 'Leppingwell', 'lleppingwell31@ustream.tv', '2024-01-04'),
	('Sandy', 'Dymock', 'sdymock4u@over-blog.com', '2024-01-04'),
	('Brandyn', 'Meah', 'bmeah6j@taobao.com', '2024-01-04'),
	('Ximenes', 'Masdon', 'xmasdon7o@reverbnation.com', '2024-01-04'),
	('Ettie', 'Revel', 'erevel82@hibu.com', '2024-01-04'),
	('Asia', 'Ellicombe', 'aellicombe87@illinois.edu', '2024-01-04'),
	('Lavinie', 'Shurey', 'lshurey8v@merriam-webster.com', '2024-01-04'),
	('Ted', 'Di Ruggiero', 'tdiruggiero98@about.me', '2024-01-04'),
	('Ham', 'Scotti', 'hscottia5@wordpress.com', '2024-01-04'),
	('Andreana', 'Goomes', 'agoomesag@wunderground.com', '2024-01-04'),
	('Corrina', 'Peattie', 'cpeattiebt@sina.com.cn', '2024-01-04'),
	('Aidan', 'Brownlie', 'abrownlieda@ucoz.com', '2024-01-04'),
	('Gaspar', 'Dignam', 'gdigname5@ebay.co.uk', '2024-01-04'),
	('Kelcey', 'Chrystal', 'kchrystaleb@wp.com', '2024-01-04'),
	('Bride', 'OHeneghan', 'boheneghanec@cbc.ca', '2024-01-04'),
	('Clayborn', 'Woodhams', 'cwoodhamsee@harvard.edu', '2024-01-04'),
	('Trenna', 'Fosdyke', 'tfosdykeev@ask.com', '2024-01-04'),
	('Shauna', 'Grouvel', 'sgrouvelge@disqus.com', '2024-01-04'),
	('Jedidiah', 'Duding', 'jdudinggf@engadget.com', '2024-01-04'),
	('Purcell', 'Albers', 'palbersgg@wordpress.org', '2024-01-04'),
	('Germaine', 'Denniston', 'gdennistonh4@europa.eu', '2024-01-04'),
	('Beckie', 'Hexter', 'bhexterhf@xing.com', '2024-01-04'),
	('Ninnette', 'Langdale', 'nlangdaleii@bizjournals.com', '2024-01-04'),
	('Justina', 'Fairest', 'jfairestix@biglobe.ne.jp', '2024-01-04'),
	('Wileen', 'Ludgrove', 'wludgroveja@ifeng.com', '2024-01-04'),
	('Ciel', 'Shaplin', 'ajlitt@hotmail.com', '2024-01-04'),
	('Malory', 'Mold', 'torgox@yahoo.com', '2024-01-04'),
	('Verine', 'Jurasek', 'wenzlaff@yahoo.com', '2024-01-04'),
	('Dani', 'Godley', 'bogjobber@hotmail.com', '2024-01-04'),
	('Charmine', 'Crottagh', 'geekoid@gmail.com', '2024-01-04'),
	('Jennee', 'Ovington', 'rupak@gmail.com', '2024-01-04'),
	('Hillary', 'Collyer', 'jyoliver@yahoo.com', '2024-01-04'),
	('Edita', 'Fishley', 'xtang@hotmail.com', '2024-01-04'),
	('Tania', 'Grinin', 'samantha.pollich@hotmail.com', '2024-01-04'),
	('Tabby', 'Leonida', 'jasmin55@yahoo.com', '2024-01-04'),
	('Kirby', 'OClery', 'zkohler@yahoo.com', '2024-01-04'),
	('Rancell', 'Clohisey', 'hreilly@gmail.com', '2024-01-04'),
	('Tamera', 'Bowling', 'roxane.kutch@hotmail.com', '2024-01-04'),
	('Hilliary', 'Alenikov', 'halenikov0@lulu.com', '2024-01-05'),
	('Carter', 'Broome', 'cbroome2@nasa.gov', '2024-01-05'),
	('Egor', 'Schulz', 'eschulz1n@loc.gov', '2024-01-05'),
	('Read', 'McGaugey', 'rmcgaugey29@prnewswire.com', '2024-01-05'),
	('Jewel', 'Cronin', 'jcronin2a@jimdo.com', '2024-01-05'),
	('Pearle', 'Loody', 'ploody30@auda.org.au', '2024-01-05'),
	('Rosanna', 'Emer', 'remer3k@clickbank.net', '2024-01-05'),
	('Kelila', 'Abbis', 'kabbis4t@tripod.com', '2024-01-05'),
	('Matty', 'Hembery', 'mhembery4z@dell.com', '2024-01-05'),
	('Stefania', 'Dybald', 'sdybald51@nationalgeographic.com', '2024-01-05'),
	('Alix', 'Krishtopaittis', 'akrishtopaittis5s@google.com.br', '2024-01-05'),
	('Bealle', 'OKinneally', 'bokinneally67@vkontakte.ru', '2024-01-05'),
	('Alvy', 'Tomet', 'atomet69@wikipedia.org', '2024-01-05'),
	('Raquel', 'Duligal', 'rduligal6b@census.gov', '2024-01-05'),
	('Rita', 'Bentham3', 'rbentham6c@virginia.edu', '2024-01-05'),
	('Sherlocke', 'Blenkinsop', 'sblenkinsop6m@mail.ru', '2024-01-05'),
	('Brana', 'Naisby', 'bnaisby70@mapquest.com', '2024-01-05'),
	('Stephen', 'MacMoyer', 'smacmoyer7u@indiatimes.com', '2024-01-05'),
	('Dick', 'Capey', 'dcapey8s@clickbank.net', '2024-01-05'),
	('Meris', 'Bambrick', 'mbambrick9k@bluehost.com', '2024-01-05'),
	('Laurel', 'Squires', 'lsquires9x@blogspot.com', '2024-01-05'),
	('Jacklin', 'Jeffels', 'jjeffelsad@tripadvisor.com', '2024-01-05'),
	('Annabela', 'Daoust', 'adaoustbu@friendfeed.com', '2024-01-05'),
	('Alix', 'Halsey', 'ahalseyc8@chron.com', '2024-01-05'),
	('Elle', 'Smallridge', 'esmallridgecv@ucoz.ru', '2024-01-05'),
	('Obed', 'Featherstonehaugh', 'ofeatherstonehaughf6@bbb.org', '2024-01-05'),
	('Waldon', 'Caudelier', 'wcaudelierfo@ucsd.edu', '2024-01-05'),
	('Markus', 'Walsom', 'mwalsomg8@constantcontact.com', '2024-01-05'),
	('Rose', 'Cunniff', 'rcunniffgc@freewebs.com', '2024-01-05'),
	('Constancy', 'Bullocke', 'cbullockei3@toplist.cz', '2024-01-05'),
	('Rosaline', 'Niblock', 'rniblockic@discovery.com', '2024-01-05'),
	('Anders', 'Walewski', 'ullman@yahoo.com', '2024-01-05'),
	('Logan', 'Sorbey', 'rhialto@hotmail.com', '2024-01-05'),
	('Elvis', 'Philip', 'dieman@gmail.com', '2024-01-05'),
	('Jo-anne', 'Bende', 'slaff@yahoo.com', '2024-01-05'),
	('Bil', 'Rayhill', 'dawnsong@yahoo.com', '2024-01-05'),
	('Katharina', 'Thurman', 'dbanarse@hotmail.com', '2024-01-05'),
	('Kaleb', 'Mahood', 'draper@gmail.com', '2024-01-05'),
	('Sheridan', 'Hundal', 'roamer@hotmail.com', '2024-01-05'),
	('Carolin', 'Stennard', 'mthurn@gmail.com', '2024-01-05'),
	('Valencia', 'Pettman', 'jugalator@yahoo.com', '2024-01-05'),
	('Onofredo', 'Kopfen', 'schimmel.ebony@yahoo.com', '2024-01-05'),
	('Cory', 'Tuffield', 'marshall09@hotmail.com', '2024-01-05'),
	('Cymbre', 'Thackston', 'huel.yolanda@hotmail.com', '2024-01-05'),
	('Livy', 'Nelhams', 'vpadberg@gmail.com', '2024-01-05'),
	('Nina', 'Yorke', 'xcarroll@gmail.com', '2024-01-05'),
	('Lenna', 'Bradnick', 'nlesch@gmail.com', '2024-01-05'),
	('Agathe', 'Tottie', 'flatley.noel@gmail.com', '2024-01-05'),
	('Rudolfo', 'Simeonov', 'rsimeonovn@arstechnica.com', '2024-01-06'),
	('Tate', 'Lavies', 'tlaviesr@shareasale.com', '2024-01-06'),
	('Randell', 'Hindhaugh', 'rhindhaugh1o@i2i.jp', '2024-01-06'),
	('Jenine', 'Beebis', 'jbeebis2o@sina.com.cn', '2024-01-06'),
	('Julietta', 'Sauter', 'jsauter33@flavors.me', '2024-01-06'),
	('Fara', 'Tewkesbury', 'ftewkesbury3e@dagondesign.com', '2024-01-06'),
	('Rafaelia', 'Baudoux', 'rbaudoux3o@over-blog.com', '2024-01-06'),
	('Consuelo', 'Randleson', 'crandleson3p@typepad.com', '2024-01-06'),
	('Burk', 'Lever', 'blever41@pagesperso-orange.fr', '2024-01-06'),
	('Tamma', 'Elcoat', 'telcoat49@army.mil', '2024-01-06'),
	('Zach', 'Felce', 'zfelce4p@fastcompany.com', '2024-01-06'),
	('Arch', 'Delucia', 'adelucia50@usa.gov', '2024-01-06'),
	('Margret', 'Pennycock', 'mpennycock5d@oakley.com', '2024-01-06'),
	('Lynne', 'Peacher', 'lpeacher5t@ucla.edu', '2024-01-06'),
	('Sofie', 'Edmundson', 'sedmundson68@prweb.com', '2024-01-06'),
	('Brew', 'Kamena', 'bkamena6n@simplemachines.org', '2024-01-06'),
	('Mortimer', 'Geall', 'mgeall7n@miitbeian.gov.cn', '2024-01-06'),
	('Raoul', 'Kubczak', 'rkubczak8q@independent.co.uk', '2024-01-06'),
	('Terrye', 'Squibb', 'tsquibb9a@mashable.com', '2024-01-06'),
	('Rennie', 'Robard', 'rrobard9r@mac.com', '2024-01-06'),
	('Mari', 'Slyme', 'mslymeau@newsvine.com', '2024-01-06'),
	('Lenora', 'Bedenham', 'lbedenhamb5@simplemachines.org', '2024-01-06'),
	('Ravid', 'Goodered', 'rgooderedbo@spotify.com', '2024-01-06'),
	('Marianne', 'Proudman', 'mproudmancd@epa.gov', '2024-01-06'),
	('Adriaens', 'Byfield', 'abyfieldcf@seattletimes.com', '2024-01-06'),
	('Malvin', 'Eagleton', 'meagletonck@drupal.org', '2024-01-06'),
	('Michelle', 'Harbach', 'mharbachd9@epa.gov', '2024-01-06'),
	('Worthy', 'Temperley', 'wtemperleydd@twitpic.com', '2024-01-06'),
	('Marnia', 'OGleasane', 'mogleasaneek@thetimes.co.uk', '2024-01-06'),
	('Loree', 'Friday', 'lfridayf1@independent.co.uk', '2024-01-06'),
	('Jody', 'Heckner', 'jhecknerfj@histats.com', '2024-01-06'),
	('Jayme', 'Denington', 'jdeningtong3@fc2.com', '2024-01-06'),
	('Ezequiel', 'Paton', 'epatonhj@eventbrite.com', '2024-01-06'),
	('Mario', 'Dundendale', 'mdundendalei4@redcross.org', '2024-01-06'),
	('Sam', 'Climar', 'sclimarj4@angelfire.com', '2024-01-06'),
	('Linn', 'Fouracres', 'lfouracresj8@ocn.ne.jp', '2024-01-06'),
	('Clementius', 'Comolli', 'camenisch@yahoo.com', '2024-01-06'),
	('Daloris', 'Dorning', 'pakaste@hotmail.com', '2024-01-06'),
	('Even', 'Richold', 'improv@gmail.com', '2024-01-06'),
	('Gerrard', 'Mapples', 'jorgb@yahoo.com', '2024-01-06'),
	('Harlene', 'Hanmer', 'harpes@gmail.com', '2024-01-06'),
	('Eduino', 'Tapner', 'mavilar@gmail.com', '2024-01-06'),
	('Gui', 'Twallin', 'axel19@yahoo.com', '2024-01-06'),
	('Hansiain', 'Foulgham', 'farrell.jacinto@gmail.com', '2024-01-06'),
	('Sybila', 'Ruddy', 'domingo83@yahoo.com', '2024-01-06'),
	('Sondra', 'Heather', 'bashirian.gene@yahoo.com', '2024-01-06'),
	('Forrest', 'Durnin', 'fdurninf@washingtonpost.com', '2024-01-07'),
	('Wilmer', 'McCuaig', 'wmccuaigw@comsenz.com', '2024-01-07'),
	('Vincent', 'Firby', 'vfirby2p@msu.edu', '2024-01-07'),
	('Kristine', 'Flowitt', 'kflowitt3z@networkadvertising.org', '2024-01-07'),
	('Susanna', 'Beglin', 'sbeglin5o@jimdo.com', '2024-01-07'),
	('Patricio', 'Eason', 'peason6p@mail.ru', '2024-01-07'),
	('Georgine', 'Batteson', 'gbatteson92@jigsy.com', '2024-01-07'),
	('Gabriell', 'Tennison', 'gtennison9c@cloudflare.com', '2024-01-07'),
	('Janeen', 'Rival', 'jrivalan@tinypic.com', '2024-01-07'),
	('Trey', 'Hardiman', 'thardimanbl@google.com.br', '2024-01-07'),
	('Roseanne', 'Linfoot', 'rlinfootbz@youtu.be', '2024-01-07'),
	('Lulita', 'Andreini', 'landreinic6@phoca.cz', '2024-01-07'),
	('Amity', 'Schruurs', 'aschruursca@timesonline.co.uk', '2024-01-07'),
	('Cindi', 'Claypool', 'cclaypoolcs@usa.gov', '2024-01-07'),
	('Ninette', 'Day', 'ndayct@stumbleupon.com', '2024-01-07'),
	('Hercules', 'McGlaud', 'hmcglaudf7@usa.gov', '2024-01-07'),
	('Derril', 'Lotterington', 'dlotteringtonf8@msn.com', '2024-01-07'),
	('Glennie', 'Toffanelli', 'gtoffanellifk@photobucket.com', '2024-01-07'),
	('Zabrina', 'Costin', 'zcostingy@etsy.com', '2024-01-07'),
	('Cassie', 'Utterson', 'cuttersonh6@umn.edu', '2024-01-07'),
	('Kassandra', 'Alennikov', 'kalennikovi5@blogs.com', '2024-01-07'),
	('Tiena', 'Rozec', 'trozecjb@myspace.com', '2024-01-07'),
	('Tova', 'Fairn', 'inico@hotmail.com', '2024-01-07'),
	('Teena', 'Bilbey', 'hling@gmail.com', '2024-01-07'),
	('Syd', 'Pert', 'crandall@hotmail.com', '2024-01-07'),
	('Mari', 'Giraudy', 'pfitza@gmail.com', '2024-01-07'),
	('Rolfe', 'Junes', 'fglock@yahoo.com', '2024-01-07'),
	('Elsy', 'Becker', 'giafly@yahoo.com', '2024-01-07'),
	('Ursola', 'Leversuch', 'pizza@yahoo.com', '2024-01-07'),
	('Krissie', 'Moyse', 'agapow@hotmail.com', '2024-01-07'),
	('Ludovika', 'Wurst', 'janet.schmitt@yahoo.com', '2024-01-07'),
	('Hieronymus', 'Edens', 'dallin31@yahoo.com', '2024-01-07'),
	('Georgeta', 'Sinnett', 'cole.joe@gmail.com', '2024-01-07'),
	('Maximo', 'Deeks', 'ujakubowski@gmail.com', '2024-01-07'),
	('Cooper', 'Dionisii', 'adolph68@gmail.com', '2024-01-07'),
	('Sammy', 'Balducci', 'sbalducci3@example.com', '2024-01-08'),
	('Burnaby', 'Farington', 'bfarington15@yellowbook.com', '2024-01-08'),
	('Marley', 'Matelaitis', 'mmatelaitis1q@lycos.com', '2024-01-08'),
	('Alis', 'Le Noury', 'alenoury23@1und1.de', '2024-01-08'),
	('Jarret', 'Jarrett', 'jjarrett2v@plala.or.jp', '2024-01-08'),
	('Dawna', 'Hulks', 'dhulks37@imageshack.us', '2024-01-08'),
	('Glenine', 'Dunstall', 'gdunstall3m@tumblr.com', '2024-01-08'),
	('Hulda', 'Daglish', 'hdaglish3y@reverbnation.com', '2024-01-08'),
	('Dolli', 'Avison', 'davison40@hc360.com', '2024-01-08'),
	('Sharron', 'Moorerud', 'smoorerud5h@nymag.com', '2024-01-08'),
	('Thelma', 'Kelcher', 'tkelcher5v@google.it', '2024-01-08'),
	('Eula', 'Lambertazzi', 'elambertazzi64@washingtonpost.com', '2024-01-08'),
	('Elisha', 'Lipscombe', 'elipscombe6u@arizona.edu', '2024-01-08'),
	('Harlene', 'Cannan', 'hcannan74@blogspot.com', '2024-01-08'),
	('Floria', 'Clayson', 'fclayson7a@booking.com', '2024-01-08'),
	('Kikelia', 'Horsfield', 'khorsfield7h@gravatar.com', '2024-01-08'),
	('Papageno', 'McCathy', 'pmccathy7p@edublogs.org', '2024-01-08'),
	('Susanne', 'Ninotti', 'sninotti8b@angelfire.com', '2024-01-08'),
	('Parsifal', 'Bassick', 'pbassicka7@hostgator.com', '2024-01-08'),
	('Lyda', 'Patriche', 'lpatricheax@cmu.edu', '2024-01-08'),
	('Keefe', 'Doleman', 'kdolemancj@behance.net', '2024-01-08'),
	('Conni', 'McCoole', 'cmccooleed@csmonitor.com', '2024-01-08'),
	('Henri', 'Earlam', 'hearlameh@w3.org', '2024-01-08'),
	('Keelia', 'Sillick', 'ksillicken@tinyurl.com', '2024-01-08'),
	('Pippo', 'Dyet', 'pdyetey@home.pl', '2024-01-08'),
	('Carree', 'Dumsday', 'cdumsdayfc@printfriendly.com', '2024-01-08'),
	('Zenia', 'Jearum', 'zjearumh1@google.de', '2024-01-08'),
	('Clotilda', 'Boog', 'cboogh5@utexas.edu', '2024-01-08'),
	('Nell', 'Ivanuschka', 'nivanuschkai1@businesswire.com', '2024-01-08'),
	('Sheree', 'Formigli', 'sformigliib@sourceforge.net', '2024-01-08'),
	('Terrijo', 'Earley', 'tearleyih@cyberchimps.com', '2024-01-08'),
	('Stanleigh', 'Holehouse', 'telbij@hotmail.com', '2024-01-08'),
	('Edik', 'Currin', 'bryam@yahoo.com', '2024-01-08'),
	('Ethelin', 'Dowgill', 'rkobes@gmail.com', '2024-01-08'),
	('Olivette', 'Nobriga', 'horrocks@gmail.com', '2024-01-08'),
	('Dun', 'Gres', 'pkplex@hotmail.com', '2024-01-08'),
	('Jessalyn', 'Yanyushkin', 'daveewart@hotmail.com', '2024-01-08'),
	('Orella', 'Brecknall', 'rsmartin@gmail.com', '2024-01-08'),
	('Bale', 'Mangenot', 'ngedmond@hotmail.com', '2024-01-08'),
	('Celle', 'Winterscale', 'hodkiewicz.haley@gmail.com', '2024-01-08'),
	('Lulita', 'Nashe', 'marks.clinton@hotmail.com', '2024-01-08'),
	('Bale', 'Cusick', 'elbert08@hotmail.com', '2024-01-08'),
	('Demott', 'Nevison', 'ibayer@gmail.com', '2024-01-08'),
	('Lombard', 'Aberdalgy', 'katelynn.schulist@yahoo.com', '2024-01-08'),
	('Angeline', 'Proschek', 'bertrand39@yahoo.com', '2024-01-08'),
	('Kaleb', 'Cohen', 'lhoppe@gmail.com', '2024-01-08'),
	('Veronika', 'Kingh', 'vkinghd@vkontakte.ru', '2024-01-09'),
	('Sharia', 'Cossum', 'scossumm@japanpost.jp', '2024-01-09'),
	('Manfred', 'Leedes', 'mleedes18@usnews.com', '2024-01-09'),
	('Sherm', 'Sooley', 'ssooley1f@e-recht24.de', '2024-01-09'),
	('Lydon', 'Royal', 'lroyal2e@about.com', '2024-01-09'),
	('Nikolai', 'Chesnut', 'nchesnut3s@deviantart.com', '2024-01-09'),
	('Chloette', 'Clitherow', 'cclitherow4e@vistaprint.com', '2024-01-09'),
	('Golda', 'Maasze', 'gmaasze5g@bbb.org', '2024-01-09'),
	('Christi', 'Richings', 'crichings5n@imgur.com', '2024-01-09'),
	('Meredith', 'Morphey', 'mmorphey5w@unesco.org', '2024-01-09'),
	('Brandon', 'McHan', 'bmchan6s@infoseek.co.jp', '2024-01-09'),
	('Elsi', 'Behning', 'ebehning6w@flickr.com', '2024-01-09'),
	('Jeremias', 'Northing', 'jnorthing73@howstuffworks.com', '2024-01-09'),
	('Clair', 'Bartoleyn', 'cbartoleyn8g@netlog.com', '2024-01-09'),
	('Royal', 'Sambiedge', 'rsambiedge94@economist.com', '2024-01-09'),
	('Eveline', 'Botterman', 'ebotterman9b@jigsy.com', '2024-01-09'),
	('Lem', 'Underwood', 'lunderwooda6@freewebs.com', '2024-01-09'),
	('Gonzalo', 'Ellyatt', 'gellyattd6@blogs.com', '2024-01-09'),
	('Dyan', 'De Minico', 'ddeminicodv@live.com', '2024-01-09'),
	('Hale', 'Glede', 'hgledee2@icq.com', '2024-01-09'),
	('Arty', 'Smithe', 'asmithee8@cbc.ca', '2024-01-09'),
	('Corabella', 'Anselm', 'canselmel@youku.com', '2024-01-09'),
	('Hi', 'Sweet', 'hsweeteo@dagondesign.com', '2024-01-09'),
	('Vida', 'Gerraty', 'vgerratyeq@nasa.gov', '2024-01-09'),
	('Constancia', 'Barme', 'cbarmees@studiopress.com', '2024-01-09'),
	('Rollins', 'Greenlies', 'rgreenliesfm@zimbio.com', '2024-01-09'),
	('Barnabas', 'Hoggan', 'bhogganfq@simplemachines.org', '2024-01-09'),
	('Stephen', 'Hinrichsen', 'shinrichsenfr@e-recht24.de', '2024-01-09'),
	('Rosita', 'Hallifax', 'rhallifaxhb@biglobe.ne.jp', '2024-01-09'),
	('Leanna', 'Beltzner', 'lbeltznerhc@google.nl', '2024-01-09'),
	('Ingelbert', 'Chastang', 'ichastanghq@arstechnica.com', '2024-01-09'),
	('Quill', 'McGriffin', 'qmcgriffinht@newyorker.com', '2024-01-09'),
	('Shanda', 'Dimock', 'sdimockij@etsy.com', '2024-01-09'),
	('Zonnya', 'Fotherby', 'zfotherbyio@youku.com', '2024-01-09'),
	('Cris', 'Cusiter', 'janneh@hotmail.com', '2024-01-09'),
	('Kingston', 'Dackombe', 'killmenow@yahoo.com', '2024-01-09'),
	('Emmet', 'Tabart', 'jshirley@gmail.com', '2024-01-09'),
	('Wilhelmina', 'McGerraghty', 'ullman@gmail.com', '2024-01-09'),
	('Waverly', 'Finlator', 'aardo@yahoo.com', '2024-01-09'),
	('Alexis', 'Simnor', 'malvar@gmail.com', '2024-01-09'),
	('Dav', 'Hansard', 'rcwil@yahoo.com', '2024-01-09'),
	('Wyn', 'de Verson', 'pat.champlin@yahoo.com', '2024-01-09'),
	('Fredric', 'Eminson', 'towne.milo@gmail.com', '2024-01-09'),
	('Ramsay', 'Pillman', 'nelson76@yahoo.com', '2024-01-09'),
	('Willa', 'Galtone', 'oma.fritsch@hotmail.com', '2024-01-09'),
	('Tadio', 'Pickford', 'vwalker@hotmail.com', '2024-01-09'),
	('Kayla', 'Winder', 'camryn.schinner@gmail.com', '2024-01-09'),
	('Joye', 'Leinweber', 'hosea.raynor@hotmail.com', '2024-01-09'),
	('Florenza', 'Battye', 'fbattye9@delicious.com', '2024-01-10'),
	('Cherlyn', 'Swindin', 'cswindine@xing.com', '2024-01-10'),
	('Christabella', 'Reidshaw', 'creidshaw1d@skyrock.com', '2024-01-10'),
	('Godfry', 'Gibbs', 'ggibbs38@miibeian.gov.cn', '2024-01-10'),
	('Henryetta', 'Ascraft', 'hascraft3r@nsw.gov.au', '2024-01-10'),
	('Michael', 'Sey', 'msey5p@uiuc.edu', '2024-01-10'),
	('Tomasina', 'Larkworthy', 'tlarkworthy5x@1und1.de', '2024-01-10'),
	('Brade', 'Gerdts', 'bgerdts6t@cdbaby.com', '2024-01-10'),
	('Shelia', 'Stoffel', 'sstoffel6v@usa.gov', '2024-01-10'),
	('Nat', 'Tansly', 'ntansly75@java.com', '2024-01-10'),
	('Thomasa', 'Adriani', 'tadriani7k@reddit.com', '2024-01-10'),
	('Paolo', 'Bromidge', 'pbromidge7m@gov.uk', '2024-01-10'),
	('Deane', 'Verlander', 'dverlander8m@narod.ru', '2024-01-10'),
	('Danya', 'Ladlow', 'dladlow8z@addthis.com', '2024-01-10'),
	('Beverly', 'Aslott', 'baslott9d@msu.edu', '2024-01-10'),
	('Estevan', 'Laffin', 'elaffin9h@meetup.com', '2024-01-10'),
	('Napoleon', 'Earpe', 'nearpe9i@cpanel.net', '2024-01-10'),
	('Haleigh', 'Duell', 'hduell9o@newyorker.com', '2024-01-10'),
	('Glad', 'Huddy', 'ghuddych@de.vu', '2024-01-10'),
	('Sloan', 'Abrahamovitz', 'sabrahamovitzcp@arizona.edu', '2024-01-10'),
	('Maud', 'Sarl', 'msarldh@utexas.edu', '2024-01-10'),
	('Angelika', 'Flucker', 'afluckerdl@bluehost.com', '2024-01-10'),
	('Filippa', 'Dyet', 'fdyetdm@hexun.com', '2024-01-10'),
	('Floris', 'Molloy', 'fmolloydo@toplist.cz', '2024-01-10'),
	('Charles', 'Brideoke', 'cbrideokee4@unicef.org', '2024-01-10'),
	('Jude', 'Norfolk', 'jnorfolkea@photobucket.com', '2024-01-10'),
	('Des', 'Benck', 'dbenckf0@webeden.co.uk', '2024-01-10'),
	('Meier', 'Capper', 'mcapperf2@lulu.com', '2024-01-10'),
	('Nance', 'Tizard', 'ntizardfh@tinypic.com', '2024-01-10'),
	('Ilyse', 'Tumilty', 'itumiltyi0@mediafire.com', '2024-01-10'),
	('Boote', 'Towsie', 'btowsiein@fastcompany.com', '2024-01-10'),
	('Calvin', 'Pfaffe', 'cpfaffeip@sphinn.com', '2024-01-10'),
	('Alicia', 'McPhillimey', 'amcphillimeyis@jigsy.com', '2024-01-10'),
	('Jillene', 'Blakely', 'parkes@gmail.com', '2024-01-10'),
	('Dan', 'Pardew', 'zavadsky@yahoo.com', '2024-01-10'),
	('Whitby', 'Slimings', 'jmorris@yahoo.com', '2024-01-10'),
	('Loralie', 'Walburn', 'dowdy@yahoo.com', '2024-01-10'),
	('Buddy', 'Lisamore', 'peoplesr@gmail.com', '2024-01-10'),
	('Noelyn', 'Machan', 'mnemonic@gmail.com', '2024-01-10'),
	('Arluene', 'Bladesmith', 'atmarks@yahoo.com', '2024-01-10'),
	('Morton', 'Stoker', 'eidac@gmail.com', '2024-01-10'),
	('Blake', 'Wight', 'dhyatt@yahoo.com', '2024-01-10'),
	('Lira', 'Orchard', 'olson.salvatore@gmail.com', '2024-01-10'),
	('Flemming', 'Sykora', 'luis.trantow@gmail.com', '2024-01-10'),
	('Morgana', 'Rolston', 'eryn94@yahoo.com', '2024-01-10'),
	('Carlye', 'Artrick', 'ward.edwina@hotmail.com', '2024-01-10'),
	('Vicky', 'Brettelle', 'kali.satterfield@hotmail.com', '2024-01-10'),
	('Webb', 'Bour', 'dayton.senger@gmail.com', '2024-01-10'),
	('Ignaz', 'Scotfurth', 'kovacek.clementine@gmail.com', '2024-01-10'),
	('Conroy', 'Milnthorpe', 'tre28@hotmail.com', '2024-01-10'),
	('Andres', 'Newarte', 'anewarte1@wufoo.com', '2024-01-11'),
	('Laney', 'Satyford', 'lsatyforda@nasa.gov', '2024-01-11'),
	('Chrisy', 'Maceur', 'cmaceur16@loc.gov', '2024-01-11'),
	('Benjie', 'Sleeny', 'bsleeny1g@de.vu', '2024-01-11'),
	('Justino', 'Collcott', 'jcollcott1m@baidu.com', '2024-01-11'),
	('Benni', 'Dreakin', 'bdreakin1v@com.com', '2024-01-11'),
	('Jay', 'Baiden', 'jbaiden2x@eepurl.com', '2024-01-11'),
	('Reider', 'Jertz', 'rjertz34@bloglines.com', '2024-01-11'),
	('Deeann', 'Gordon', 'dgordon3j@answers.com', '2024-01-11'),
	('Torre', 'Amerighi', 'tamerighi47@dion.ne.jp', '2024-01-11'),
	('Berti', 'Moncaster', 'bmoncaster4l@gov.uk', '2024-01-11'),
	('Leelah', 'Wibberley', 'lwibberley4w@163.com', '2024-01-11'),
	('Julianna', 'MacCaffery', 'jmaccaffery5u@stanford.edu', '2024-01-11'),
	('Tonye', 'Heigho', 'theigho89@bigcartel.com', '2024-01-11'),
	('Danyelle', 'Sarginson', 'dsarginson8d@friendfeed.com', '2024-01-11'),
	('Chane', 'Hirtzmann', 'chirtzmann9y@omniture.com', '2024-01-11'),
	('Tobey', 'Allum', 'tallumaj@stumbleupon.com', '2024-01-11'),
	('Dana', 'Matthewman', 'dmatthewmanc9@360.cn', '2024-01-11'),
	('Marion', 'Archbell', 'marchbellcr@comsenz.com', '2024-01-11'),
	('Blane', 'Rapps', 'brappsdg@lycos.com', '2024-01-11'),
	('Dene', 'Iannelli', 'diannelligp@squidoo.com', '2024-01-11'),
	('Loria', 'Blaase', 'lblaaseig@npr.org', '2024-01-11'),
	('Mindy', 'Sheara', 'mshearaj1@altervista.org', '2024-01-11'),
	('Vera', 'Daleman', 'vdalemanjc@php.net', '2024-01-11'),
	('Roxy', 'Covill', 'murdocj@gmail.com', '2024-01-11'),
	('Mitchel', 'Wigfield', 'attwood@yahoo.com', '2024-01-11'),
	('Raynell', 'Skill', 'ovprit@yahoo.com', '2024-01-11'),
	('Arda', 'Poulson', 'mcast@yahoo.com', '2024-01-11'),
	('Aline', 'Hunnisett', 'solomon@gmail.com', '2024-01-11'),
	('Gherardo', 'Hawken', 'dgatwood@gmail.com', '2024-01-11'),
	('Harlan', 'Rigge', 'jcholewa@hotmail.com', '2024-01-11'),
	('Basilius', 'Cundey', 'cathrine.gorczany@yahoo.com', '2024-01-11'),
	('Laurel', 'Skiplorne', 'murray.vivienne@gmail.com', '2024-01-11'),
	('Kelcey', 'Corinton', 'murray.mercedes@hotmail.com', '2024-01-11'),
	('Quinton', 'Fyndon', 'august26@hotmail.com', '2024-01-11'),
	('Jesselyn', 'Branford', 'tsipes@gmail.com', '2024-01-11'),
	('Darcey', 'Trotman', 'satterfield.hobart@gmail.com', '2024-01-11'),
	('Lonni', 'Sproston', 'lsprostono@bigcartel.com', '2024-01-12'),
	('Filberte', 'Scuffham', 'fscuffham14@ow.ly', '2024-01-12'),
	('Gerianne', 'Exell', 'gexell24@fastcompany.com', '2024-01-12'),
	('Dela', 'Hammerman', 'dhammerman2n@answers.com', '2024-01-12'),
	('Bibby', 'Walling', 'bwalling2r@issuu.com', '2024-01-12'),
	('Kerrie', 'Currall', 'kcurrall2w@imageshack.us', '2024-01-12'),
	('Francyne', 'Terzo', 'fterzo46@youku.com', '2024-01-12'),
	('Benoit', 'Bowlands', 'bbowlands4d@fda.gov', '2024-01-12'),
	('Genevra', 'Mitie', 'gmitie4f@google.com.br', '2024-01-12'),
	('Gaylord', 'Fawlo', 'gfawlo7c@liveinternet.ru', '2024-01-12'),
	('Fernanda', 'Threadgould', 'fthreadgould7q@ca.gov', '2024-01-12'),
	('Adam', 'Plumptre', 'aplumptre8f@phpbb.com', '2024-01-12'),
	('Genvieve', 'Orton', 'gorton8j@umich.edu', '2024-01-12'),
	('Lucinda', 'Stork', 'lstork90@theatlantic.com', '2024-01-12'),
	('Adelbert', 'Pendry', 'apendry9u@who.int', '2024-01-12'),
	('Adda', 'Duchart', 'aduchartaa@plala.or.jp', '2024-01-12'),
	('Cortie', 'Junkison', 'cjunkisonac@marriott.com', '2024-01-12'),
	('Arch', 'OFinan', 'aofinanae@instagram.com', '2024-01-12'),
	('Jane', 'Hargitt', 'jhargittb4@unc.edu', '2024-01-12'),
	('Lura', 'Oby', 'lobybd@samsung.com', '2024-01-12'),
	('Chris', 'Zecchetti', 'czecchettibh@reverbnation.com', '2024-01-12'),
	('Bennett', 'MacInnes', 'bmacinnescx@cnet.com', '2024-01-12'),
	('Leonie', 'Demongeot', 'ldemongeotcy@t-online.de', '2024-01-12'),
	('Winny', 'Cawdell', 'wcawdellde@eepurl.com', '2024-01-12'),
	('Cirstoforo', 'Tipler', 'ctiplerdt@bravesites.com', '2024-01-12'),
	('Pepito', 'Scala', 'pscalaf4@apache.org', '2024-01-12'),
	('Licha', 'McVee', 'lmcveefd@toplist.cz', '2024-01-12'),
	('Kellsie', 'Shelborne', 'kshelborneg1@yellowbook.com', '2024-01-12'),
	('Daisey', 'OSkehan', 'doskehangh@aol.com', '2024-01-12'),
	('Amabel', 'Haydock', 'ahaydockh8@newsvine.com', '2024-01-12'),
	('Tobit', 'Bompas', 'tbompashg@auda.org.au', '2024-01-12'),
	('Jourdain', 'Breitler', 'jbreitlerit@sina.com.cn', '2024-01-12'),
	('Korry', 'Chander', 'kchanderj7@economist.com', '2024-01-12'),
	('Gill', 'Paramore', 'durist@yahoo.com', '2024-01-12'),
	('Meagan', 'Annable', 'cvrcek@hotmail.com', '2024-01-12'),
	('Emmy', 'Coy', 'ntegrity@gmail.com', '2024-01-12'),
	('Iseabal', 'Cuffin', 'gravyface@hotmail.com', '2024-01-12'),
	('Wernher', 'Collicott', 'birddog@gmail.com', '2024-01-12'),
	('Pearle', 'Mawdsley', 'singer@yahoo.com', '2024-01-12'),
	('Bill', 'Vannuchi', 'eryn.steuber@yahoo.com', '2024-01-12'),
	('Morly', 'Klemmt', 'royce.bashirian@gmail.com', '2024-01-12'),
	('Lynn', 'Volante', 'roel.barrows@gmail.com', '2024-01-12'),
	('Morgun', 'Guirardin', 'braun.peggie@yahoo.com', '2024-01-12'),
	('Chloe', 'Hamley', 'kohler.darrion@hotmail.com', '2024-01-12'),
	('Munroe', 'MacCallester', 'dorothea.herman@gmail.com', '2024-01-12'),
	('Delia', 'Lace', 'alfonzo.leuschke@yahoo.com', '2024-01-12'),
	('Elisabeth', 'Bedingfield', 'ebedingfieldv@blogspot.com', '2024-01-13'),
	('Astra', 'Kunkel', 'akunkel19@mapy.cz', '2024-01-13'),
	('Ayn', 'Kitchenside', 'akitchenside1i@ucoz.ru', '2024-01-13'),
	('Ethel', 'Chsteney', 'echsteney1l@oakley.com', '2024-01-13'),
	('Gerty', 'Rowney', 'growney20@google.co.uk', '2024-01-13'),
	('Hermon', 'Winscum', 'hwinscum2b@earthlink.net', '2024-01-13'),
	('Minnaminnie', 'Nowell', 'mnowell2d@blog.com', '2024-01-13'),
	('Inna', 'Wiszniewski', 'iwiszniewski3q@timesonline.co.uk', '2024-01-13'),
	('Alayne', 'Mullender', 'amullender3v@friendfeed.com', '2024-01-13'),
	('Biddie', 'Pee', 'bpee4m@samsung.com', '2024-01-13'),
	('Jasmine', 'Warrier', 'jwarrier4r@miitbeian.gov.cn', '2024-01-13'),
	('Kipper', 'Cushion', 'kcushion59@sogou.com', '2024-01-13'),
	('Elie', 'Skip', 'eskip5m@sourceforge.net', '2024-01-13'),
	('Grantley', 'Chisnell', 'gchisnell6f@smh.com.au', '2024-01-13'),
	('Kristin', 'Wolfindale', 'kwolfindale6h@oaic.gov.au', '2024-01-13'),
	('Annaliese', 'Neylon', 'aneylon6q@discuz.net', '2024-01-13'),
	('Brandyn', 'Bryson', 'bbryson7e@wisc.edu', '2024-01-13'),
	('Heidie', 'Gajewski', 'hgajewski7x@loc.gov', '2024-01-13'),
	('Hatti', 'Jirasek', 'hjirasek81@yolasite.com', '2024-01-13'),
	('Marci', 'Yearne', 'myearne9t@slate.com', '2024-01-13'),
	('Carrol', 'Grinaugh', 'cgrinaugha1@instagram.com', '2024-01-13'),
	('Isaac', 'Ambrozik', 'iambrozikal@ucla.edu', '2024-01-13'),
	('Melicent', 'Wooldridge', 'mwooldridgeb6@usa.gov', '2024-01-13'),
	('Emmaline', 'Cristofari', 'ecristofarid0@hao123.com', '2024-01-13'),
	('Gayler', 'Brody', 'gbrodyd2@usa.gov', '2024-01-13'),
	('Hewet', 'Bamborough', 'hbamboroughdi@bloglines.com', '2024-01-13'),
	('Sapphira', 'Gammett', 'sgammettdu@psu.edu', '2024-01-13'),
	('Oona', 'Benedek', 'obenedekep@alexa.com', '2024-01-13'),
	('Tory', 'Guterson', 'tgutersonf9@joomla.org', '2024-01-13'),
	('Panchito', 'Drexel', 'pdrexelgj@freewebs.com', '2024-01-13'),
	('Corinna', 'Doggerell', 'cdoggerellgv@columbia.edu', '2024-01-13'),
	('Mischa', 'Thick', 'mthickh0@time.com', '2024-01-13'),
	('Rita', 'Darko', 'rdarkohr@wikia.com', '2024-01-13'),
	('Idalina', 'Wedge', 'iwedgei9@bloglovin.com', '2024-01-13'),
	('Pietro', 'Witling', 'pwitlingir@hatena.ne.jp', '2024-01-13'),
	('Nanon', 'Stanners', 'nstannersiw@360.cn', '2024-01-13'),
	('Anetta', 'Blundin', 'syrinx@hotmail.com', '2024-01-13'),
	('Meredith', 'Braybrooks', 'milton@gmail.com', '2024-01-13'),
	('Minne', 'Selvey', 'jusdisgi@gmail.com', '2024-01-13'),
	('Cullie', 'Cleen', 'rsmartin@yahoo.com', '2024-01-13'),
	('Mauricio', 'Insko', 'bartak@hotmail.com', '2024-01-13'),
	('Lanni', 'Headey', 'malin@gmail.com', '2024-01-13'),
	('Alvy', 'Davidavidovics', 'staikos@hotmail.com', '2024-01-13'),
	('Deborah', 'Ilem', 'jkegl@hotmail.com', '2024-01-13'),
	('Cointon', 'Calderon', 'gloria.rogahn@yahoo.com', '2024-01-13'),
	('Richardo', 'Frankema', 'roberts.ignacio@gmail.com', '2024-01-13'),
	('Nerissa', 'Retallack', 'tschmitt@gmail.com', '2024-01-13'),
	('Michel', 'Wadsworth', 'mwadsworthj@jimdo.com', '2024-01-14'),
	('Marta', 'Brandacci', 'mbrandacciq@webs.com', '2024-01-14'),
	('Erika', 'Diamond', 'ediamondu@google.com.au', '2024-01-14'),
	('Antoinette', 'Darracott', 'adarracott13@indiatimes.com', '2024-01-14'),
	('Page', 'Lackie', 'plackie1r@who.int', '2024-01-14'),
	('Svend', 'Crewe', 'screwe28@stanford.edu', '2024-01-14'),
	('Kandace', 'Faichney', 'kfaichney2i@microsoft.com', '2024-01-14'),
	('Adolf', 'Guihen', 'aguihen2z@storify.com', '2024-01-14'),
	('Mitzi', 'Aynold', 'maynold32@wordpress.org', '2024-01-14'),
	('Keelia', 'Daen', 'kdaen3w@163.com', '2024-01-14'),
	('Diannne', 'Gouldeby', 'dgouldeby48@rakuten.co.jp', '2024-01-14'),
	('Huntlee', 'Mitcham', 'hmitcham53@cornell.edu', '2024-01-14'),
	('Jacynth', 'MacCaughey', 'jmaccaughey55@posterous.com', '2024-01-14'),
	('George', 'Course', 'gcourse5r@amazon.co.uk', '2024-01-14'),
	('Orlando', 'Lidyard', 'olidyard6y@reddit.com', '2024-01-14'),
	('Conway', 'Antonescu', 'cantonescu8t@feedburner.com', '2024-01-14'),
	('Ashbey', 'Wesgate', 'awesgate9p@php.net', '2024-01-14'),
	('Jaime', 'Edgworth', 'jedgwortha9@opera.com', '2024-01-14'),
	('Nicolis', 'Jacks', 'njacksbb@bbc.co.uk', '2024-01-14'),
	('Ahmed', 'Jahnisch', 'ajahnischbe@live.com', '2024-01-14'),
	('Darcy', 'Elliman', 'dellimanbf@lulu.com', '2024-01-14'),
	('Noellyn', 'Lapthorn', 'nlapthornc5@statcounter.com', '2024-01-14'),
	('Symon', 'Portis', 'sportiscu@google.nl', '2024-01-14'),
	('Elissa', 'Bemand', 'ebemandd1@photobucket.com', '2024-01-14'),
	('Bernette', 'Rewbottom', 'brewbottomd5@bloglines.com', '2024-01-14'),
	('Samuel', 'Olesen', 'solesendf@timesonline.co.uk', '2024-01-14'),
	('Gaspard', 'Ladon', 'gladonds@marriott.com', '2024-01-14'),
	('Stoddard', 'Knewstub', 'sknewstubej@hostgator.com', '2024-01-14'),
	('Kelci', 'Farries', 'kfarriesf3@kickstarter.com', '2024-01-14'),
	('Belicia', 'Ashard', 'bashardfl@ft.com', '2024-01-14'),
	('Helli', 'Vlasyuk', 'hvlasyukg0@edublogs.org', '2024-01-14'),
	('Stephan', 'Bleasby', 'sbleasbygt@paypal.com', '2024-01-14'),
	('Zitella', 'Bailles', 'zbaillesgz@rediff.com', '2024-01-14'),
	('Melosa', 'Abrami', 'tjensen@gmail.com', '2024-01-14'),
	('Flinn', 'Lydiate', 'pdbaby@gmail.com', '2024-01-14'),
	('Del', 'Coton', 'pdbaby@hotmail.com', '2024-01-14'),
	('Alfred', 'Noot', 'wikinerd@hotmail.com', '2024-01-14'),
	('Jorrie', 'Cleaver', 'rtanter@yahoo.com', '2024-01-14'),
	('Odo', 'Shoard', 'jessica55@hotmail.com', '2024-01-14'),
	('Darlleen', 'Ebbings', 'lesch.clay@hotmail.com', '2024-01-14'),
	('Chicky', 'Fedder', 'schoen.harry@yahoo.com', '2024-01-14'),
	('Anallese', 'Androsik', 'stokes.jaylen@yahoo.com', '2024-01-14'),
	('Michaela', 'Bagnell', 'schoen.sanford@hotmail.com', '2024-01-14'),
	('Henriette', 'Batha', 'lindsey.windler@hotmail.com', '2024-01-14'),
	('Nancy', 'McAuley', 'talia03@hotmail.com', '2024-01-14'),
	('Rosalind', 'Kuhlmey', 'zulauf.elenora@hotmail.com', '2024-01-14'),
	('Sisile', 'Innott', 'evans@hotmail.com', '2024-01-14'),
	('Micheal', 'Slatter', 'mslattery@hc360.com', '2024-01-15'),
	('Carin', 'Rohlfing', 'crohlfing2k@wsj.com', '2024-01-15'),
	('Pammi', 'Popping', 'ppopping2y@sbwire.com', '2024-01-15'),
	('Abbie', 'Cotgrove', 'acotgrove4j@bloglovin.com', '2024-01-15'),
	('Fanchette', 'Koomar', 'fkoomar4k@netscape.com', '2024-01-15'),
	('Leroy', 'Swindells', 'lswindells4s@bluehost.com', '2024-01-15'),
	('Donella', 'OClery', 'doclery5e@tinyurl.com', '2024-01-15'),
	('Fredia', 'Clyde', 'fclyde6l@geocities.com', '2024-01-15'),
	('Jeannine', 'Patching', 'jpatching72@163.com', '2024-01-15'),
	('Charmane', 'Cuming', 'ccuming76@netlog.com', '2024-01-15'),
	('Murdoch', 'Brokenbrow', 'mbrokenbrow8h@sohu.com', '2024-01-15'),
	('Farlee', 'Stearn', 'fstearn8o@github.io', '2024-01-15'),
	('Kial', 'Lestor', 'klestor9n@drupal.org', '2024-01-15'),
	('Alvan', 'Guisot', 'aguisota3@narod.ru', '2024-01-15'),
	('Scotty', 'Barnby', 'sbarnbyaw@pagesperso-orange.fr', '2024-01-15'),
	('Nealy', 'Websdale', 'nwebsdaleb7@xinhuanet.com', '2024-01-15'),
	('Theadora', 'Kubalek', 'tkubalekc4@weather.com', '2024-01-15'),
	('Malchy', 'Tolputt', 'mtolputtcb@google.nl', '2024-01-15'),
	('Stanislaus', 'Thackeray', 'sthackeraydr@digg.com', '2024-01-15'),
	('Julienne', 'Olufsen', 'jolufsenfu@arstechnica.com', '2024-01-15'),
	('Teddie', 'Gillian', 'tgilliangi@amazonaws.com', '2024-01-15'),
	('Killy', 'Laurance', 'klaurancegq@latimes.com', '2024-01-15'),
	('Lannie', 'Yeardsley', 'lyeardsleygr@spotify.com', '2024-01-15'),
	('Emery', 'Wilds', 'ewildsha@nbcnews.com', '2024-01-15'),
	('Brody', 'Aitcheson', 'baitchesonhd@godaddy.com', '2024-01-15'),
	('Jonell', 'Harrold', 'jharroldho@nba.com', '2024-01-15'),
	('Hillyer', 'Corden', 'hcordenhx@indiatimes.com', '2024-01-15'),
	('Lyndell', 'Dymond', 'ldymondim@hexun.com', '2024-01-15'),
	('Torrie', 'Fleet', 'tfleetje@360.cn', '2024-01-15'),
	('Yorgo', 'Chene', 'vmalik@hotmail.com', '2024-01-15'),
	('Anica', 'Krabbe', 'crypt@hotmail.com', '2024-01-15'),
	('Natty', 'Dockray', 'quantaman@yahoo.com', '2024-01-15'),
	('Florenza', 'Littlepage', 'pemungkah@yahoo.com', '2024-01-15'),
	('Franky', 'Karel', 'fukuchi@yahoo.com', '2024-01-15'),
	('Gibby', 'Quennell', 'staikos@gmail.com', '2024-01-15'),
	('Lorettalorna', 'Killby', 'gordonjcp@hotmail.com', '2024-01-15'),
	('Alina', 'Shillito', 'mrobshaw@gmail.com', '2024-01-15'),
	('Kalil', 'Nana', 'dwheeler@yahoo.com', '2024-01-15'),
	('Tanitansy', 'Seston', 'padberg.aurelio@yahoo.com', '2024-01-15'),
	('Laurice', 'Spicer', 'kemmer.amani@hotmail.com', '2024-01-15'),
	('Ryley', 'Chalcot', 'bernier.brionna@gmail.com', '2024-01-15'),
	('Iago', 'Snalham', 'kozey.britney@hotmail.com', '2024-01-15'),
	('Sheba', 'Slobom', 'earnestine.feeney@yahoo.com', '2024-01-15'),
	('Andie', 'Simeons', 'joanne.thompson@hotmail.com', '2024-01-15'),
	('Margalit', 'Mattessen', 'mac.glover@gmail.com', '2024-01-15'),
	('Corbin', 'Maher', 'abbott.maurine@yahoo.com', '2024-01-15'),
	('Rivi', 'Rennicks', 'dorthy18@hotmail.com', '2024-01-15'),
	('Helen', 'Kusick', 'hkusickc@guardian.co.uk', '2024-01-16'),
	('Eliot', 'Syfax', 'esyfax2h@arstechnica.com', '2024-01-16'),
	('Troy', 'Carde', 'tcarde2u@uol.com.br', '2024-01-16'),
	('Brigid', 'Picott', 'bpicott3t@over-blog.com', '2024-01-16'),
	('Felicdad', 'Girodier', 'fgirodier4g@time.com', '2024-01-16'),
	('Brandea', 'Colten', 'bcolten4y@acquirethisname.com', '2024-01-16'),
	('Olivier', 'Windross', 'owindross52@gov.uk', '2024-01-16'),
	('Chad', 'Wheal', 'cwheal56@gnu.org', '2024-01-16'),
	('Alejoa', 'Beaby', 'abeaby5b@skype.com', '2024-01-16'),
	('Leia', 'Waight', 'lwaight5j@altervista.org', '2024-01-16'),
	('Petey', 'Harral', 'pharral6r@cdbaby.com', '2024-01-16'),
	('Dinnie', 'Kilford', 'dkilford7i@noaa.gov', '2024-01-16'),
	('Sven', 'Gahagan', 'sgahagan8k@amazon.com', '2024-01-16'),
	('Teresa', 'Curnokk', 'tcurnokk8y@de.vu', '2024-01-16'),
	('Moises', 'Saphin', 'msaphin91@bloglovin.com', '2024-01-16'),
	('Chadd', 'McGuiness', 'cmcguiness99@dedecms.com', '2024-01-16'),
	('Cad', 'Smaling', 'csmaling9m@wordpress.com', '2024-01-16'),
	('Clay', 'Sommerfeld', 'csommerfeldbi@yahoo.com', '2024-01-16'),
	('Rory', 'Moyer', 'rmoyerbx@goo.ne.jp', '2024-01-16'),
	('Carlynne', 'Grindall', 'cgrindallc0@eepurl.com', '2024-01-16'),
	('Ugo', 'Atyea', 'uatyeac1@smh.com.au', '2024-01-16'),
	('Rafferty', 'Adess', 'radesscq@sciencedaily.com', '2024-01-16'),
	('Christos', 'Kislingbury', 'ckislingburyew@google.es', '2024-01-16'),
	('Mellisa', 'Wabe', 'mwabefi@cargocollective.com', '2024-01-16'),
	('Salvidor', 'Hodcroft', 'shodcroftgb@woothemes.com', '2024-01-16'),
	('Corrina', 'Mylechreest', 'cmylechreesthh@amazon.co.uk', '2024-01-16'),
	('Marylee', 'Gypson', 'mgypsoni8@storify.com', '2024-01-16'),
	('Marchall', 'Embleton', 'membletonie@squarespace.com', '2024-01-16'),
	('Daniella', 'Tregien', 'dwendlan@yahoo.com', '2024-01-16'),
	('Grannie', 'Barkway', 'charity98@yahoo.com', '2024-01-16'),
	('Sal', 'Snoddin', 'konopelski.emma@hotmail.com', '2024-01-16'),
	('Mady', 'Davids', 'tremblay.berta@gmail.com', '2024-01-16'),
	('Fonsie', 'Ekkel', 'francesca.vandervort@yahoo.com', '2024-01-16'),
	('Janeen', 'Woolcocks', 'ukshlerin@gmail.com', '2024-01-16'),
	('Cara', 'Le Strange', 'yundt.alice@gmail.com', '2024-01-16'),
	('Roarke', 'Allin', 'nelle92@hotmail.com', '2024-01-16'),
	('Hebert', 'Cohn', 'gavin.gislason@hotmail.com', '2024-01-16'),
	('Rey', 'Brobak', 'golda86@gmail.com', '2024-01-16'),
	('Maddie', 'Waberer', 'reichert.roy@hotmail.com', '2024-01-16'),
	('Adelaide', 'Carville', 'jayson.bayer@hotmail.com', '2024-01-16'),
	('Emyle', 'Archdeacon', 'earchdeacon8@ow.ly', '2024-01-17'),
	('Teddie', 'MacKilroe', 'tmackilroei@jigsy.com', '2024-01-17'),
	('Ned', 'Gwinnell', 'ngwinnell11@amazon.com', '2024-01-17'),
	('Rania', 'Offell', 'roffell12@forbes.com', '2024-01-17'),
	('Amity', 'Tarplee', 'atarplee1a@fastcompany.com', '2024-01-17'),
	('Juliane', 'MattiCCI', 'jmatticci1c@dropbox.com', '2024-01-17'),
	('Jacky', 'Demougeot', 'jdemougeot1j@networksolutions.com', '2024-01-17'),
	('Retha', 'Kinde', 'rkinde2q@taobao.com', '2024-01-17'),
	('Mandi', 'Obray', 'mobray3n@wp.com', '2024-01-17'),
	('Bennett', 'Gummie', 'bgummie42@bigcartel.com', '2024-01-17'),
	('Ilario', 'MacAlaster', 'imacalaster45@google.pl', '2024-01-17'),
	('Elvyn', 'Radcliffe', 'eradcliffe4i@unicef.org', '2024-01-17'),
	('Michale', 'Sartin', 'msartin4v@artisteer.com', '2024-01-17'),
	('Corbet', 'Dignum', 'cdignum5k@constantcontact.com', '2024-01-17'),
	('Gerald', 'Everton', 'geverton5y@indiegogo.com', '2024-01-17'),
	('Ashleigh', 'Moreman', 'amoreman79@biglobe.ne.jp', '2024-01-17'),
	('Antin', 'Doodson', 'adoodson7f@nature.com', '2024-01-17'),
	('Joscelin', 'Lythgoe', 'jlythgoe7g@blogspot.com', '2024-01-17'),
	('Eadmund', 'Northage', 'enorthage84@spiegel.de', '2024-01-17'),
	('Alexandr', 'Champe', 'achampe9j@123-reg.co.uk', '2024-01-17'),
	('Manolo', 'Buntain', 'mbuntain9v@geocities.jp', '2024-01-17'),
	('Kristien', 'Gorstidge', 'kgorstidgea4@dagondesign.com', '2024-01-17'),
	('Tami', 'Spelling', 'tspellingaq@sbwire.com', '2024-01-17'),
	('Bobby', 'Silverwood', 'bsilverwoodb1@oaic.gov.au', '2024-01-17'),
	('Coraline', 'Cansfield', 'ccansfieldbq@google.co.jp', '2024-01-17'),
	('Lev', 'Edmund', 'ledmundfa@wired.com', '2024-01-17'),
	('Verena', 'Shucksmith', 'vshucksmithfn@adobe.com', '2024-01-17'),
	('Nicolina', 'McNirlan', 'nmcnirlanfy@qq.com', '2024-01-17'),
	('Ardella', 'Peyes', 'apeyesg5@geocities.jp', '2024-01-17'),
	('Letizia', 'Dionisii', 'ldionisiih3@diigo.com', '2024-01-17'),
	('Gretal', 'Scoggins', 'gscogginshs@feedburner.com', '2024-01-17'),
	('Grier', 'Conville', 'gconvillei6@lulu.com', '2024-01-17'),
	('Christian', 'Tomisch', 'flaviog@gmail.com', '2024-01-17'),
	('Saree', 'Sulter', 'whimsy@yahoo.com', '2024-01-17'),
	('Merla', 'Francomb', 'debest@yahoo.com', '2024-01-17'),
	('Hugo', 'Antrum', 'openldap@gmail.com', '2024-01-17'),
	('Cornie', 'Fenelow', 'pjaskolski@hotmail.com', '2024-01-17'),
	('Lucy', 'Howorth', 'gquitzon@gmail.com', '2024-01-17'),
	('Nariko', 'Mattecot', 'lauryn.marvin@hotmail.com', '2024-01-17'),
	('Terrill', 'Brimilcombe', 'emilio.stokes@gmail.com', '2024-01-17'),
	('Henrik', 'Minker', 'pete.gutmann@hotmail.com', '2024-01-17'),
	('Quinn', 'Biaggioni', 'stan34@yahoo.com', '2024-01-17'),
	('Fredi', 'Lineker', 'jaskolski.kole@gmail.com', '2024-01-17'),
	('Moll', 'Mollett', 'mmollettb@4shared.com', '2024-01-18'),
	('Bale', 'Burgis', 'bburgiss@blog.com', '2024-01-18'),
	('Dagny', 'Abthorpe', 'dabthorpe1z@t-online.de', '2024-01-18'),
	('Dino', 'Kirkebye', 'dkirkebye36@fda.gov', '2024-01-18'),
	('Fritz', 'Tyzack', 'ftyzack3d@fda.gov', '2024-01-18'),
	('Maybelle', 'Gunby', 'mgunby3g@unc.edu', '2024-01-18'),
	('Clare', 'Lickess', 'clickess3h@independent.co.uk', '2024-01-18'),
	('Darrelle', 'Dahlborg', 'ddahlborg3i@shop-pro.jp', '2024-01-18'),
	('Hildegarde', 'Aimson', 'haimson5z@wsj.com', '2024-01-18'),
	('Isidore', 'Goodbar', 'igoodbar60@creativecommons.org', '2024-01-18'),
	('Jerome', 'Cloake', 'jcloake65@yahoo.com', '2024-01-18'),
	('Gayelord', 'Treby', 'gtreby6a@unc.edu', '2024-01-18'),
	('Benedict', 'Raffles', 'braffles71@hubpages.com', '2024-01-18'),
	('Sal', 'Odd', 'sodd7r@examiner.com', '2024-01-18'),
	('Lizzy', 'Jendrassik', 'ljendrassik9e@msn.com', '2024-01-18'),
	('Reider', 'Lowen', 'rlowen9q@ox.ac.uk', '2024-01-18'),
	('Mala', 'Rablan', 'mrablan9s@amazonaws.com', '2024-01-18'),
	('Burton', 'Thomesson', 'bthomesson9w@bigcartel.com', '2024-01-18'),
	('Rey', 'Cregan', 'rcreganab@netlog.com', '2024-01-18'),
	('Terri', 'Gomersall', 'tgomersallb0@quantcast.com', '2024-01-18'),
	('Megan', 'Castlake', 'mcastlakeb2@dailymail.co.uk', '2024-01-18'),
	('Pat', 'Gwyther', 'pgwytherba@nytimes.com', '2024-01-18'),
	('Osborne', 'Adamsson', 'oadamssonbm@clickbank.net', '2024-01-18'),
	('Corney', 'Lifsey', 'clifseyby@wp.com', '2024-01-18'),
	('Marga', 'Boodell', 'mboodellcg@spiegel.de', '2024-01-18'),
	('Gwenni', 'Cattroll', 'gcattrollcl@wikia.com', '2024-01-18'),
	('Sheri', 'Ruzic', 'sruziccn@apple.com', '2024-01-18'),
	('Parnell', 'McEneny', 'pmcenenyd7@weebly.com', '2024-01-18'),
	('Torin', 'Bolduc', 'tbolducdz@mapy.cz', '2024-01-18'),
	('Una', 'de Guise', 'udeguisee1@berkeley.edu', '2024-01-18'),
	('Nada', 'Heustice', 'nheusticee9@dell.com', '2024-01-18'),
	('Eolande', 'Dishman', 'edishmaner@cnet.com', '2024-01-18'),
	('Meier', 'Durbridge', 'mdurbridgefb@blinklist.com', '2024-01-18'),
	('Darleen', 'Charrington', 'dcharringtong2@domainmarket.com', '2024-01-18'),
	('Christie', 'Kalkofer', 'ckalkofergn@sina.com.cn', '2024-01-18'),
	('Esra', 'Dmych', 'edmychhp@homestead.com', '2024-01-18'),
	('Auria', 'Habbert', 'ahabbertil@uol.com.br', '2024-01-18'),
	('Kimble', 'Kinglake', 'kkinglakeiq@google.com.hk', '2024-01-18'),
	('Eartha', 'Zanelli', 'ezanellij2@freewebs.com', '2024-01-18'),
	('Romeo', 'Attiwill', 'rattiwillj3@usda.gov', '2024-01-18'),
	('Crystie', 'Atley', 'aprakash@yahoo.com', '2024-01-18'),
	('Engracia', 'Fabbro', 'jshirley@yahoo.com', '2024-01-18'),
	('Marga', 'Scintsbury', 'pthomsen@hotmail.com', '2024-01-18'),
	('Nettle', 'Southerill', 'parsimony@gmail.com', '2024-01-18'),
	('Minda', 'Joerning', 'loscar@gmail.com', '2024-01-18'),
	('Gwenette', 'Thys', 'ssmitham@yahoo.com', '2024-01-18'),
	('Gena', 'Learmouth', 'kaden02@gmail.com', '2024-01-18'),
	('Giacinta', 'Dupree', 'obahringer@hotmail.com', '2024-01-18'),
	('Francine', 'Burnard', 'maribel.considine@hotmail.com', '2024-01-18'),
	('Kizzee', 'Pfeifer', 'demetrius04@hotmail.com', '2024-01-18'),
	('Roosevelt', 'Arnley', 'daniel.orlando@yahoo.com', '2024-01-18'),
	('Denys', 'Lescop', 'dlescoph@4shared.com', '2024-01-19'),
	('Amaleta', 'Dahlback', 'adahlback1t@behance.net', '2024-01-19'),
	('Tandie', 'Pettecrew', 'tpettecrew1u@about.me', '2024-01-19'),
	('Alexandros', 'Vanichkin', 'avanichkin2f@uol.com.br', '2024-01-19'),
	('Elizabet', 'Sibylla', 'esibylla2l@marketwatch.com', '2024-01-19'),
	('Somerset', 'Grocock', 'sgrocock35@paypal.com', '2024-01-19'),
	('Pegeen', 'Bryson', 'pbryson39@wix.com', '2024-01-19'),
	('Peyter', 'Toone', 'ptoone3c@rambler.ru', '2024-01-19'),
	('Gael', 'Lewer', 'glewer3f@samsung.com', '2024-01-19'),
	('Elizabeth', 'Luty', 'eluty5i@dyndns.org', '2024-01-19'),
	('Karna', 'Rosling', 'krosling63@reddit.com', '2024-01-19'),
	('Zilvia', 'Swarbrigg', 'zswarbrigg6e@oakley.com', '2024-01-19'),
	('Jud', 'Nuscha', 'jnuscha7b@homestead.com', '2024-01-19'),
	('Corly', 'Germain', 'cgermain7d@mashable.com', '2024-01-19'),
	('Matthaeus', 'Witherspoon', 'mwitherspoon7l@youtu.be', '2024-01-19'),
	('Erda', 'Cud', 'ecud8n@devhub.com', '2024-01-19'),
	('Nat', 'Cassam', 'ncassam8p@privacy.gov.au', '2024-01-19'),
	('Imogene', 'Prettyman', 'iprettyman9f@uol.com.br', '2024-01-19'),
	('Alicia', 'Winger', 'awinger9l@smugmug.com', '2024-01-19'),
	('Lay', 'Murrie', 'lmurrieai@wikimedia.org', '2024-01-19'),
	('Tremayne', 'Wales', 'twalesb9@geocities.com', '2024-01-19'),
	('Alexandra', 'Buzzing', 'abuzzingbg@ted.com', '2024-01-19'),
	('Tasha', 'Klimpke', 'tklimpkebj@shareasale.com', '2024-01-19'),
	('Ingrid', 'Holttom', 'iholttombs@icq.com', '2024-01-19'),
	('Libbey', 'Caras', 'lcarascm@exblog.jp', '2024-01-19'),
	('Sanderson', 'Gillatt', 'sgillattd8@xrea.com', '2024-01-19'),
	('Georgie', 'Batkin', 'gbatkindx@slashdot.org', '2024-01-19'),
	('Olimpia', 'Vannini', 'ovanninifv@sciencedirect.com', '2024-01-19'),
	('Albie', 'Terrelly', 'aterrellyfx@sitemeter.com', '2024-01-19'),
	('Esme', 'Standbrooke', 'estandbrookeg4@moonfruit.com', '2024-01-19'),
	('Megen', 'Mallinder', 'mmallinderhl@seattletimes.com', '2024-01-19'),
	('Philip', 'Fleis', 'pfleisid@mashable.com', '2024-01-19'),
	('Octavia', 'Ingleby', 'oinglebyiu@nyu.edu', '2024-01-19'),
	('Goddard', 'Gregh', 'ggreghj5@networksolutions.com', '2024-01-19'),
	('Bibbye', 'Barclay', 'bbarclayjf@topsy.com', '2024-01-19'),
	('Fred', 'Pinnigar', 'seebs@yahoo.com', '2024-01-19'),
	('Zaria', 'Dunkerley', 'cisugrad@hotmail.com', '2024-01-19'),
	('Gerhard', 'Antonopoulos', 'emcleod@gmail.com', '2024-01-19'),
	('Denna', 'Woodson', 'daveewart@gmail.com', '2024-01-19'),
	('Jo ann', 'Bellham', 'jimxugle@yahoo.com', '2024-01-19'),
	('Bill', 'Macoun', 'malvar@hotmail.com', '2024-01-19'),
	('Marla', 'Lunn', 'akoblin@hotmail.com', '2024-01-19'),
	('Mischa', 'Henfre', 'delpha.hammes@yahoo.com', '2024-01-19'),
	('Ardella', 'Erb', 'justice.ferry@yahoo.com', '2024-01-19'),
	('Renata', 'Freshwater', 'ypfannerstill@gmail.com', '2024-01-19'),
	('Ive', 'Antognetti', 'wintheiser.marian@hotmail.com', '2024-01-19'),
	('Malcolm', 'Cirlos', 'pouros.jeffry@yahoo.com', '2024-01-19'),
	('Nariko', 'Beville', 'leon.reynolds@hotmail.com', '2024-01-19'),
	('Natalie', 'Mingasson', 'devin28@gmail.com', '2024-01-19'),
	('Benjie', 'Bess', 'bbess5@hao123.com', '2024-01-20'),
	('Gus', 'Musprat', 'gmusprat7@narod.ru', '2024-01-20'),
	('Constance', 'Brickett', 'cbrickettx@whitehouse.gov', '2024-01-20'),
	('Abby', 'Verralls', 'averralls1b@furl.net', '2024-01-20'),
	('Carlina', 'Beincken', 'cbeincken25@dagondesign.com', '2024-01-20'),
	('Bartlet', 'Bawles', 'bbawles2c@myspace.com', '2024-01-20'),
	('Herminia', 'Crowhurst', 'hcrowhurst3a@deviantart.com', '2024-01-20'),
	('Duffy', 'Hardson', 'dhardson3l@over-blog.com', '2024-01-20'),
	('Stephenie', 'Arlett', 'sarlett43@mediafire.com', '2024-01-20'),
	('Biddy', 'Connechy', 'bconnechy4b@diigo.com', '2024-01-20'),
	('Merilee', 'Stigell', 'mstigell4c@i2i.jp', '2024-01-20'),
	('Chariot', 'Bess', 'cbess4h@multiply.com', '2024-01-20'),
	('Perle', 'Del Castello', 'pdelcastello4n@mac.com', '2024-01-20'),
	('Ava', 'Clibbery', 'aclibbery4q@behance.net', '2024-01-20'),
	('Brennen', 'Glasser', 'bglasser5a@vinaora.com', '2024-01-20'),
	('Kary', 'Alton', 'kalton66@slate.com', '2024-01-20'),
	('Joaquin', 'Pilkinton', 'jpilkinton77@ihg.com', '2024-01-20'),
	('Dorie', 'Signorelli', 'dsignorelli8a@amazonaws.com', '2024-01-20'),
	('Siward', 'Gammett', 'sgammett9g@yelp.com', '2024-01-20'),
	('Hastings', 'Websdale', 'hwebsdalea0@twitpic.com', '2024-01-20'),
	('Grover', 'Adelman', 'gadelmanaf@blogspot.com', '2024-01-20'),
	('Audi', 'Oleksinski', 'aoleksinskiav@gmpg.org', '2024-01-20'),
	('Austin', 'Ryles', 'arylesaz@marriott.com', '2024-01-20'),
	('Mar', 'Lindroos', 'mlindroosbv@booking.com', '2024-01-20'),
	('Evangelin', 'Castagne', 'ecastagnec2@sun.com', '2024-01-20'),
	('Lucias', 'Thring', 'lthringce@oracle.com', '2024-01-20'),
	('Linet', 'Gellion', 'lgellionco@marketwatch.com', '2024-01-20'),
	('Paulo', 'McFadden', 'pmcfaddencw@disqus.com', '2024-01-20'),
	('Caria', 'Van Merwe', 'cvanmerwecz@mozilla.com', '2024-01-20'),
	('Gerianne', 'Rostron', 'grostrond4@ox.ac.uk', '2024-01-20'),
	('Anstice', 'Biddles', 'abiddlesdk@cbslocal.com', '2024-01-20'),
	('Philip', 'Mulliner', 'pmullinerdp@cocolog-nifty.com', '2024-01-20'),
	('Nadia', 'Kilfedder', 'nkilfedderdq@nyu.edu', '2024-01-20'),
	('Heida', 'Lettice', 'hletticedw@homestead.com', '2024-01-20'),
	('Butch', 'O Kelleher', 'bokelleherdy@spiegel.de', '2024-01-20'),
	('Aridatha', 'Perview', 'aperviewfe@epa.gov', '2024-01-20'),
	('Lauralee', 'Brocklehurst', 'lbrocklehurstgs@ifeng.com', '2024-01-20'),
	('Juan', 'Erbain', 'jerbainj9@alibaba.com', '2024-01-20'),
	('Dev', 'Lytell', 'dinther@yahoo.com', '2024-01-20'),
	('Griz', 'Torrent', 'jbarta@yahoo.com', '2024-01-20'),
	('Erny', 'Kretschmer', 'ylchang@hotmail.com', '2024-01-20'),
	('Vaughn', 'Patridge', 'valdez@gmail.com', '2024-01-20'),
	('Averil', 'Benettini', 'sriha@hotmail.com', '2024-01-20'),
	('Valida', 'Wilton', 'gomor@gmail.com', '2024-01-20'),
	('Jameson', 'Twine', 'martyloo@yahoo.com', '2024-01-20'),
	('Lynde', 'Connechy', 'mcast@yahoo.com', '2024-01-20'),
	('Francesca', 'Purser', 'paolo80@hotmail.com', '2024-01-20'),
	('Toiboid', 'Aylward', 'graciela.macejkovic@hotmail.com', '2024-01-20'),
	('Shelba', 'Banting', 'eloisa77@gmail.com', '2024-01-20'),
	('Jessamyn', 'Goodred', 'verna20@gmail.com', '2024-01-20'),
	('Zulema', 'Shellum', 'ericka28@gmail.com', '2024-01-20'),
	('Gay', 'Matcham', 'gmatchaml@cnn.com', '2024-01-21'),
	('Nancee', 'Noli', 'nnolip@odnoklassniki.ru', '2024-01-21'),
	('Darb', 'Ashdown', 'dashdown2g@upenn.edu', '2024-01-21'),
	('Wes', 'Kernaghan', 'wkernaghan2m@psu.edu', '2024-01-21'),
	('Jamil', 'Thirlaway', 'jthirlaway4a@elpais.com', '2024-01-21'),
	('Nathanil', 'Coundley', 'ncoundley4x@narod.ru', '2024-01-21'),
	('Hymie', 'Verick', 'hverick57@shop-pro.jp', '2024-01-21'),
	('Georgianne', 'Bulteel', 'gbulteel58@canalblog.com', '2024-01-21'),
	('Ronny', 'Mussilli', 'rmussilli6g@barnesandnoble.com', '2024-01-21'),
	('Charlie', 'Kliche', 'ckliche6k@reference.com', '2024-01-21'),
	('Montague', 'Halden', 'mhalden6o@berkeley.edu', '2024-01-21'),
	('Niel', 'Sirett', 'nsirett85@fda.gov', '2024-01-21'),
	('Pearl', 'Cockerill', 'pcockerill8r@mac.com', '2024-01-21'),
	('Angel', 'Farquharson', 'afarquharsonak@webmd.com', '2024-01-21'),
	('Garnette', 'Villaron', 'gvillaronao@archive.org', '2024-01-21'),
	('Vern', 'Copping', 'vcoppingas@virginia.edu', '2024-01-21'),
	('Morty', 'Manes', 'mmanesbk@house.gov', '2024-01-21'),
	('Christoffer', 'Standidge', 'cstandidgec7@redcross.org', '2024-01-21'),
	('Nell', 'Kilius', 'nkiliusci@blogs.com', '2024-01-21'),
	('Yolanda', 'Pritchard', 'ypritcharddn@spotify.com', '2024-01-21'),
	('Adey', 'Birrane', 'abirranee3@businessweek.com', '2024-01-21'),
	('Janetta', 'Sunley', 'jsunleyeg@nasa.gov', '2024-01-21'),
	('Kristin', 'Smale', 'ksmaleez@reuters.com', '2024-01-21'),
	('Jakob', 'Anstead', 'jansteadfw@wordpress.com', '2024-01-21'),
	('Odille', 'Charnick', 'ocharnickfz@soup.io', '2024-01-21'),
	('Amandy', 'Yaldren', 'ayaldreng6@pcworld.com', '2024-01-21'),
	('Carroll', 'Arstall', 'carstallg7@abc.net.au', '2024-01-21'),
	('Silvanus', 'Scholtz', 'sscholtzgd@1und1.de', '2024-01-21'),
	('Hallie', 'Janda', 'hjandago@jalbum.net', '2024-01-21'),
	('Pasquale', 'Auguste', 'paugustegw@cnn.com', '2024-01-21'),
	('Sheeree', 'Carnachen', 'scarnachengx@chron.com', '2024-01-21'),
	('Augustine', 'Stell', 'astellhm@zimbio.com', '2024-01-21'),
	('Emmalynn', 'Hewkin', 'ehewkinhz@wix.com', '2024-01-21'),
	('Payton', 'Boatwright', 'pboatwrighti2@economist.com', '2024-01-21'),
	('Atlante', 'Pickston', 'apickstoni7@scribd.com', '2024-01-21'),
	('Ginger', 'Misson', 'gmissoniv@deliciousdays.com', '2024-01-21'),
	('Tito', 'Evason', 'tevasonj0@springer.com', '2024-01-21'),
	('Theodosia', 'Scarfe', 'tscarfej6@adobe.com', '2024-01-21'),
	('Lammond', 'Caseborne', 'jsnover@gmail.com', '2024-01-21'),
	('Mathilda', 'Stranks', 'agolomsh@yahoo.com', '2024-01-21'),
	('Jase', 'Bruggeman', 'schwaang@hotmail.com', '2024-01-21'),
	('Philomena', 'Smallcombe', 'mrobshaw@gmail.com', '2024-01-21'),
	('Ozzie', 'Antonijevic', 'crobles@yahoo.com', '2024-01-21'),
	('Tabbie', 'Hughf', 'bowmanbs@gmail.com', '2024-01-21'),
	('Stacy', 'Reye', 'hager@gmail.com', '2024-01-21'),
	('Lyda', 'Boord', 'xcummings@yahoo.com', '2024-01-21'),
	('Orren', 'Tatlow', 'zemlak.lisa@gmail.com', '2024-01-21'),
	('Jefferey', 'Handes', 'marco.harber@yahoo.com', '2024-01-21'),
	('Carlita', 'Durward', 'cdurward10@narod.ru', '2024-01-22'),
	('Hardy', 'Sloper', 'hsloper1k@ycombinator.com', '2024-01-22'),
	('Harcourt', 'Jerisch', 'hjerisch1s@ovh.net', '2024-01-22'),
	('Gui', 'Dulwitch', 'gdulwitch1w@dailymail.co.uk', '2024-01-22'),
	('Cleveland', 'Kulver', 'ckulver3x@goodreads.com', '2024-01-22'),
	('Gabriel', 'McKeney', 'gmckeney44@i2i.jp', '2024-01-22'),
	('Cindra', 'Pennacci', 'cpennacci4o@home.pl', '2024-01-22'),
	('Reinaldo', 'Thorndycraft', 'rthorndycraft5f@uiuc.edu', '2024-01-22'),
	('Ethelbert', 'Campa', 'ecampa5l@netlog.com', '2024-01-22'),
	('Nikaniki', 'Sanderson', 'nsanderson6d@webeden.co.uk', '2024-01-22'),
	('Donnajean', 'Carrigan', 'dcarrigan6x@toplist.cz', '2024-01-22'),
	('Hope', 'Vibert', 'hvibert7t@wix.com', '2024-01-22'),
	('Tiebout', 'Hutcheon', 'thutcheon80@indiatimes.com', '2024-01-22'),
	('Edwin', 'Yitzhak', 'eyitzhak88@mit.edu', '2024-01-22'),
	('Essy', 'Paradine', 'eparadine8e@pen.io', '2024-01-22'),
	('Helge', 'Terram', 'hterram8w@dailymotion.com', '2024-01-22'),
	('Peria', 'Lage', 'plage8x@mysql.com', '2024-01-22'),
	('Mariel', 'Grzegorzewski', 'mgrzegorzewski9z@xing.com', '2024-01-22'),
	('Clari', 'Brookwood', 'cbrookwoodam@unesco.org', '2024-01-22'),
	('Dolf', 'Abernethy', 'dabernethybn@woothemes.com', '2024-01-22'),
	('Dallas', 'McCraine', 'dmccrainecc@gmpg.org', '2024-01-22'),
	('Janelle', 'Fozzard', 'jfozzarddb@shop-pro.jp', '2024-01-22'),
	('Emmett', 'Bencher', 'ebencherdc@loc.gov', '2024-01-22'),
	('Mercy', 'Yesichev', 'myesichevef@noaa.gov', '2024-01-22'),
	('Morris', 'Savoury', 'msavouryei@hp.com', '2024-01-22'),
	('Sascha', 'Crumby', 'scrumbyfg@timesonline.co.uk', '2024-01-22'),
	('Rhys', 'McKimmie', 'rmckimmieft@theglobeandmail.com', '2024-01-22'),
	('Starla', 'Everly', 'severlygm@sohu.com', '2024-01-22'),
	('Karin', 'Iacomettii', 'kiacomettiihk@vk.com', '2024-01-22'),
	('Elisabet', 'Garthshore', 'egarthshorehw@usatoday.com', '2024-01-22'),
	('Jillene', 'Kisar', 'jkisaria@ox.ac.uk', '2024-01-22'),
	('Jerry', 'Reyes', 'jreyesif@1688.com', '2024-01-22'),
	('Merrily', 'Batts', 'mbattsik@ucoz.com', '2024-01-22'),
	('Flora', 'Matthensen', 'euice@yahoo.com', '2024-01-22'),
	('Emylee', 'Dover', 'mbrown@hotmail.com', '2024-01-22'),
	('Monika', 'Hodinton', 'graham@gmail.com', '2024-01-22'),
	('Andriette', 'Dast', 'bhima@hotmail.com', '2024-01-22'),
	('Robina', 'Moss', 'killmenow@gmail.com', '2024-01-22'),
	('Staford', 'Ashfull', 'scarlet@yahoo.com', '2024-01-22'),
	('Petronille', 'Manifold', 'imogene79@yahoo.com', '2024-01-22'),
	('Conrad', 'Keslake', 'gudrun.kilback@yahoo.com', '2024-01-22'),
	('Katuscha', 'Girault', 'shakira95@hotmail.com', '2024-01-22'),
	('Odey', 'Pinchback', 'reyna.wuckert@yahoo.com', '2024-01-22'),
	('Alicia', 'Brumwell', 'aurore.haley@yahoo.com', '2024-01-22'),
	('Marja', 'Bilbie', 'deja.damore@gmail.com', '2024-01-22'),
	('Emmy', 'Shury', 'carrie59@gmail.com', '2024-01-22'),
	('Manny', 'Chalcroft', 'satterfield.louie@gmail.com', '2024-01-22'),
	('George', 'Kelcher', 'ruben45@hotmail.com', '2024-01-22');
```


Or download as a csv:

```{r, echo = FALSE}
download_file(
  path = "data/bot_registrations_clean.csv",
  button_label = "Download user registration data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```



-----

### 2. Money Laundering

> We've identified user 7804 suspicious of money laundering and need your help in tracing the funds!

> Can you follow the money he sent all the way to the final receiver (i.e., the last person receiving the money)?

Here's the top 10 rows:

```{sql, connection = 'sqlconn'}
SELECT TOP 10 *
FROM ml_payments
ORDER BY payment_date
```

And here's the code to generate the table (you can find a copy symbol on the right top of the code chunk):

```{sql, eval=  FALSE, attr.source='style="max-height: 200px;overflow: scroll;"', connection='sqlconn'}
-- drop table ml_payments;

CREATE TABLE ml_payments(
   from_user    VARCHAR(4) NOT NULL PRIMARY KEY
  ,to_user      VARCHAR(4) NOT NULL
  ,amount       INTEGER  NOT NULL
  ,payment_date DATETIME  NOT NULL
);
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7804','4360',200,'2023-02-28T22:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1237','5790',242,'2023-02-28T22:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5363','7800',241,'2023-02-28T22:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6382','5619',224,'2023-02-28T22:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7962','2729',184,'2023-02-28T23:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6165','5363',170,'2023-02-28T23:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2165','2502',198,'2023-02-28T23:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5867','8562',285,'2023-02-28T23:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2021','4386',253,'2023-03-01T00:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1378','6818',264,'2023-03-01T00:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4360','7503',199,'2023-03-01T00:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4192','6165',223,'2023-03-01T00:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7764','7226',226,'2023-03-01T01:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5517','7962',294,'2023-03-01T01:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1150','2021',297,'2023-03-01T01:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2502','6816',262,'2023-03-01T01:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9990','2625',177,'2023-03-01T02:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7503','6491',198,'2023-03-01T02:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('547','7800',283,'2023-03-01T02:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2021','8319',208,'2023-03-01T02:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('355','976',212,'2023-03-01T03:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3113','928',172,'2023-03-01T03:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4056','7498',155,'2023-03-01T03:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2508','5867',286,'2023-03-01T03:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2135','672',280,'2023-03-01T04:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4241','4386',245,'2023-03-01T04:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2587','5517',184,'2023-03-01T04:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6491','3037',198,'2023-03-01T04:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2021','4111',260,'2023-03-01T05:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9003','3113',169,'2023-03-01T05:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6675','3440',279,'2023-03-01T05:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8193','976',189,'2023-03-01T05:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6382','6914',300,'2023-03-01T06:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4463','1657',279,'2023-03-01T06:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1416','8562',181,'2023-03-01T06:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3037','9484',198,'2023-03-01T06:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1416','4111',162,'2023-03-01T07:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2502','4386',212,'2023-03-01T07:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5669','6286',267,'2023-03-01T07:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8889','928',153,'2023-03-01T07:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4915','3113',284,'2023-03-01T08:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8319','9249',240,'2023-03-01T08:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4400','9990',204,'2023-03-01T08:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4241','8074',258,'2023-03-01T08:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9492','9816',265,'2023-03-01T09:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2135','8074',188,'2023-03-01T09:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9484','2885',197,'2023-03-01T09:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('870','9207',259,'2023-03-01T09:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5948','4896',260,'2023-03-01T10:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7764','4478',182,'2023-03-01T10:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6818','7949',150,'2023-03-01T10:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6765','547',216,'2023-03-01T10:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6818','2784',221,'2023-03-01T11:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2885','1841',196,'2023-03-01T11:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5669','4056',223,'2023-03-01T11:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('392','6862',287,'2023-03-01T11:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5067','7869',253,'2023-03-01T12:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7962','2700',177,'2023-03-01T12:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6675','1867',178,'2023-03-01T12:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4056','7111',197,'2023-03-01T12:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2729','5948',244,'2023-03-01T13:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9249','6382',208,'2023-03-01T13:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('258','4241',274,'2023-03-01T13:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1841','7627',196,'2023-03-01T13:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1408','7520',281,'2023-03-01T14:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2502','7190',264,'2023-03-01T14:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9725','8889',221,'2023-03-01T14:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3900','1101',178,'2023-03-01T14:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3113','870',295,'2023-03-01T15:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('657','2587',150,'2023-03-01T15:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6862','4463',278,'2023-03-01T15:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5669','2135',207,'2023-03-01T15:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7627','5923',196,'2023-03-01T16:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2700','9207',150,'2023-03-01T16:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7687','1408',295,'2023-03-01T16:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9492','6313',162,'2023-03-01T16:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4719','1733',272,'2023-03-01T17:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6165','180',274,'2023-03-01T17:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2587','5616',195,'2023-03-01T17:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5923','9464',195,'2023-03-01T17:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1101','5517',259,'2023-03-01T18:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4478','6286',172,'2023-03-01T18:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9725','2502',227,'2023-03-01T18:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6313','9098',186,'2023-03-01T18:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4426','1867',275,'2023-03-01T19:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4478','392',268,'2023-03-01T19:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2587','4200',179,'2023-03-01T19:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7226','4386',255,'2023-03-01T19:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4400','392',206,'2023-03-01T20:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9464','781',194,'2023-03-01T20:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2625','500',162,'2023-03-01T20:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1101','9962',218,'2023-03-01T20:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3900','9098',155,'2023-03-01T21:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2318','4937',213,'2023-03-01T21:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('781','7364',194,'2023-03-01T21:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2318','4247',245,'2023-03-01T21:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('9962','2165',212,'2023-03-01T22:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1867','9098',200,'2023-03-01T22:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2135','163',272,'2023-03-01T22:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5669','4156',234,'2023-03-01T22:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2381','4426',233,'2023-03-01T23:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4200','2021',211,'2023-03-01T23:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('392','6862',258,'2023-03-01T23:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('954','3440',274,'2023-03-01T23:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7364','191',194,'2023-03-02T00:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6862','180',298,'2023-03-02T00:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8193','9249',259,'2023-03-02T00:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('672','2165',236,'2023-03-02T00:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2135','8474',162,'2023-03-02T01:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('191','1577',193,'2023-03-02T01:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1094','3113',251,'2023-03-02T01:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1133','1416',203,'2023-03-02T01:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2700','7949',233,'2023-03-02T02:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('500','3669',242,'2023-03-02T02:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8074','3302',180,'2023-03-02T02:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('163','2502',286,'2023-03-02T02:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1237','4719',299,'2023-03-02T03:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1577','2921',192,'2023-03-02T03:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4200','7800',241,'2023-03-02T03:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6765','9272',181,'2023-03-02T03:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4719','3669',257,'2023-03-02T04:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3900','5867',195,'2023-03-02T04:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7558','2502',187,'2023-03-02T04:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2508','1733',157,'2023-03-02T04:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('180','7241',168,'2023-03-02T05:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4463','2700',271,'2023-03-02T05:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2921','6093',192,'2023-03-02T05:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5790','9003',231,'2023-03-02T05:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1378','2165',180,'2023-03-02T06:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4247','552',216,'2023-03-02T06:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7449','2165',171,'2023-03-02T06:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7869','4400',258,'2023-03-02T06:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4111','8474',176,'2023-03-02T07:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6093','3423',192,'2023-03-02T07:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('657','928',273,'2023-03-02T07:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5013','1733',176,'2023-03-02T07:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8193','7869',174,'2023-03-02T08:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('592','8319',225,'2023-03-02T08:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4386','4192',254,'2023-03-02T08:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('954','7800',192,'2023-03-02T08:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4937','258',209,'2023-03-02T09:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2587','7800',160,'2023-03-02T09:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8647','1657',194,'2023-03-02T09:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('3423','5649',191,'2023-03-02T09:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4478','7498',233,'2023-03-02T10:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7764','5669',163,'2023-03-02T10:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('180','4719',183,'2023-03-02T10:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4478','6862',152,'2023-03-02T10:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('928','7791',169,'2023-03-02T11:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5649','1721',190,'2023-03-02T11:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('8193','7449',165,'2023-03-02T11:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7241','7687',226,'2023-03-02T11:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6914','7687',202,'2023-03-02T12:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7226','592',172,'2023-03-02T12:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2700','9990',277,'2023-03-02T12:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2625','2784',237,'2023-03-02T12:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2508','5948',162,'2023-03-02T13:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2135','8193',255,'2023-03-02T13:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4400','6675',276,'2023-03-02T13:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6675','928',247,'2023-03-02T13:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6816','1867',291,'2023-03-02T14:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('547','4247',295,'2023-03-02T14:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('5517','7962',274,'2023-03-02T14:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('1721','NA',190,'2023-03-02T14:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('4056','2508',224,'2023-03-02T15:00:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('7498','1657',221,'2023-03-02T15:15:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('6862','8889',274,'2023-03-02T15:30:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('2021','6675',185,'2023-03-02T15:45:00Z');
INSERT INTO ml_payments(from_user,to_user,amount,payment_date) VALUES ('954','1408',158,'2023-03-02T16:00:00Z');



```


Or download as a csv:

```{r, echo = FALSE}
download_file(
  path = "data/ml.csv",
  button_label = "Download payments data",
  button_type = "default",
  has_icon = TRUE,
  icon = "fa fa-save",
  self_contained = FALSE
)
```

```{r, echo = FALSE}
dbDisconnect(sqlconn)
```

